---
title: "Does Your Gain Define My Loss?: Socially-Defined Counterfactual Loss and Prevention-Focused Decision-Making (Supplementary Materials)"
author: "[Anonymized for Blind Peer Review]"
output:
  pdf_document:
    toc: true
    toc_depth: 3
header-includes:
   - \usepackage[utf8]{inputenc}
   - \DeclareUnicodeCharacter{2588}{-}
bibliography      : ["rfcfloss.bib"]
---

```{r setup, include=FALSE}
set.seed(1234)
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = normalizePath('../'))
```

# Data Loading and Cleaning

## Load Libraries and Define Functions

All code used to load libraries and define functions can be found in the .Rmd file used to generate this PDF.

```{r libs, warning = FALSE, message = FALSE, include=FALSE}
# For easy reference, installation code for packages used in this manuscript that are not available on CRAN:
# devtools::install_github("crsh/papaja") # Required to produce APA-formatted manuscript

library(knitr) # Required for knitting
library(papaja) # Required for APA template
library(citr) # Required for easy insertion of citations
library(tidyverse) # Required for data cleaning
library(broman) # Required for myround() function that doesn't truncate digits
library(formatR) # Required for data cleaning (throws error otherwise)
library(psych) # Required to calculate Cronbach's alpha
library(cocron) # Required to statistically compare Cronbach's alphas
library(broom) # Required to extract effects from models
library(rIP) # Required to filter out fraudulent M-Turk participants
library(ggplot2) # Required for plots
library(jtools) # Required for simple slopes and Johnson-Neyman analysis
library(cowplot) # Required for sim_slopes
library(Hmisc) # Required for correlation matrix
library(kableExtra) # Required for table styling
library(boot) # Required for bootstrapping CIs in mediation analysis
library(lavaan) # Required for mediation analyses
library(semPlot) # Required to plot mediation models

summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
                      conf.interval=.95, .drop=TRUE) {
    library(plyr)

    # New version of length which can handle NA's: if na.rm==T, don't count them
    length2 <- function (x, na.rm=FALSE) {
        if (na.rm) sum(!is.na(x))
        else       length(x)
    }

    # This does the summary. For each group's data frame, return a vector with
    # N, mean, and sd
    datac <- ddply(data, groupvars, .drop=.drop,
      .fun = function(xx, col) {
        c(N    = length2(xx[[col]], na.rm=na.rm),
          mean = mean   (xx[[col]], na.rm=na.rm),
          sd   = sd     (xx[[col]], na.rm=na.rm)
        )
      },
      measurevar
    )

    # Rename the "mean" column    
    datac <- rename(datac, c("mean" = measurevar))

    datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean

    # Confidence interval multiplier for standard error
    # Calculate t-statistic for confidence interval: 
    # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
    ciMult <- qt(conf.interval/2 + .5, datac$N-1)
    datac$ci <- datac$se * ciMult

    return(datac)
}

pval <- function(x) {
  if (x >= .05) {
  result <- "n.s."
  }
  else if (x < .05 & x >= .01) {
  result <- "p < .05"
  }
  else if (x < .01 & x >= .001) {
  result <- "p < .01"
  }
  else {
  result <- "p < .001"
  }
  return(result)
}

```

## Import and Clean Data

All code used to import and clean data can be found in the .Rmd file used to generate this PDF. Please note: To reproduce the reported results and ensure all code runs properly, the raw dataset should be exported from Qualtrics with the *numeric values* (**not** *choice text*) option selected.

``` {r load.data, include = FALSE}
# Only loading this RData file so blockornot dataframe is loaded, as it can't be rerun without a user key:
load("data/rfcfloss_clean.RData")
# All other data is reloaded and recleaned below
```

```{r import, include=FALSE}
cfl <- read.csv(file="data/rfcfloss_raw.csv", header = TRUE)
```

```{r clean, include=FALSE, tidy = TRUE}
# Deleting two unnecessary additional header rows from Qualtrics export:
cfl <- cfl[-which(cfl$StartDate == "Start Date"), ] # Repeated header row with column names
cfl <- cfl[-1,] # Header row with Qualtrics code in curly brackets

# Renaming columns for ease of use
names(cfl) <- gsub(x = names(cfl), pattern = "\\.", replacement = "")
names(cfl) <- gsub(x = names(cfl), pattern = "rfq", replacement = "rfq_")
names(cfl) <- gsub(x = names(cfl), pattern = "rmq_rmq_", replacement = "rmq_")
colnames(cfl)[colnames(cfl) == "bit_easy"] <- "easy"
colnames(cfl)[colnames(cfl) == "bit_perf_clear"] <- "clear"
colnames(cfl)[colnames(cfl) == "bit_perf_affect"] <- "perfaffected"
colnames(cfl)[colnames(cfl) == "prev_bit"] <- "previnvested"

# Combining Bitcoin allocation (and relevant metadata) for two conditions
cfl$allo <- paste(cfl$bit_ctr_1,cfl$bit_cfl_11)
cfl$allo_timer <- paste(cfl$bit_timer_PageSubmit,cfl$bit_timer_PageSubmit1)
cfl$allo_clicks <- paste(cfl$bit_timer_ClickCount,cfl$bit_timer_ClickCount1)

# Ensuring proper data types for analysis
cfl <- droplevels(cfl) # Drop unneeded factor levels resulting from old Qualtrics headers
cfl.num <- c("Progress", "Durationinseconds", "rmq_1", "rmq_2", "rmq_3", "rmq_4", "rmq_5", "rmq_6", "rmq_7",
             "rmq_8", "rmq_9", "rmq_10", "rmq_11", "rmq_12", "rmq_13", "rmq_14", "rmq_15", "rmq_16", "rmq_17",
             "rmq_18", "rmq_19", "rmq_20", "rmq_21", "rmq_22", "rmq_23", "rmq_24", "rmq_25", "rmq_26", "rmq_27",
             "rmq_28", "rmq_29", "rmq_30", "rfq_1", "rfq_2", "rfq_3", "rfq_4", "rfq_5", "rfq_6",
             "rfq_7", "rfq_8", "rfq_9", "rfq_10", "rfq_11", "easy", "clear", "perfaffected",
             "missedout", "regret", "investearlier", "happier", "relieved", "age", "allo", "allo_timer", "allo_clicks") # Define numeric columns
cfl[cfl.num] <- lapply(cfl[cfl.num], as.character) # Convert numeric columns to character (before numeric) to prevent values from changing
cfl[cfl.num] <- lapply(cfl[cfl.num], as.numeric) # Convert numeric columns to numeric
rm(cfl.num) # Clear cfl.num from workspace as it is no longer needed

# Renaming and ordering factor levels where appropriate
cfl$gender <- as.character(cfl$gender)
cfl$gender[cfl$gender == "1"] <- "male"
cfl$gender[cfl$gender == "2"] <- "female"
cfl$gender[cfl$gender == "3"] <- "other"
cfl$gender <- as.factor(cfl$gender)

cfl$language <- as.character(cfl$language)
cfl$language[cfl$language == "1"] <- "english"
cfl$language[cfl$language == "2"] <- "spanish"
cfl$language[cfl$language == "3"] <- "other"
cfl$language <- as.factor(cfl$language)

cfl$ethnicity <- as.character(cfl$ethnicity)
cfl$ethnicity[!(cfl$ethnicity == "1" | cfl$ethnicity == "2" | cfl$ethnicity == "3" |
                  cfl$ethnicity == "4" | cfl$ethnicity == "5" | cfl$ethnicity == "6" |
                  cfl$ethnicity == "7" | is.na(cfl$ethnicity) == TRUE)] <- "multi"
cfl$ethnicity[cfl$ethnicity == "1"] <- "amerindian"
cfl$ethnicity[cfl$ethnicity == "2"] <- "asian"
cfl$ethnicity[cfl$ethnicity == "3"] <- "black"
cfl$ethnicity[cfl$ethnicity == "4"] <- "hispanic"
cfl$ethnicity[cfl$ethnicity == "5"] <- "pacislander"
cfl$ethnicity[cfl$ethnicity == "6"] <- "white"
cfl$ethnicity[cfl$ethnicity == "7"] <- "other"
cfl$ethnicity <- as.factor(cfl$ethnicity)

cfl$education <- as.character(cfl$education)
cfl$education[cfl$education == "0"] <- "none"
cfl$education[cfl$education == "1"] <- "elementary"
cfl$education[cfl$education == "2"] <- "somehs"
cfl$education[cfl$education == "3"] <- "highschool"
cfl$education[cfl$education == "4"] <- "somecollege"
cfl$education[cfl$education == "5"] <- "associates"
cfl$education[cfl$education == "6"] <- "bachelors"
cfl$education[cfl$education == "7"] <- "graddegree"
cfl$education[cfl$education == "8"] <- "doctorate"
cfl$education <- as.factor(cfl$education)
cfl$education <- factor(cfl$education, ordered = TRUE, levels = c("none", "elementary", "somehs", "highschool", "somecollege", "associates", "bachelors", "graddegree", "doctorate", "noanswer"))

cfl$income <- as.character(cfl$income)
cfl$income[cfl$income == "Prefer not to answer"] <- NA
cfl$income[cfl$income == "0"] <- "$0-$10K"
cfl$income[cfl$income == "1"] <- "$10K-$20K"
cfl$income[cfl$income == "2"] <- "$20K-$40K"
cfl$income[cfl$income == "3"] <- "$40K-$70K"
cfl$income[cfl$income == "4"] <- "$70K-$100K"
cfl$income[cfl$income == "5"] <- "$100K-$250K"
cfl$income[cfl$income == "6"] <- "$250K-$500K"
cfl$income[cfl$income == "7"] <- "$500K+"
cfl$income <- as.factor(cfl$income)
cfl$income <- factor(cfl$income, ordered = TRUE, levels = c("$0-$10K", "$10K-$20K", "$20K-$40K", "$40K-$70K", "$70K-$100K", "$100K-$250K", "$250K-$500K", "$500K+", "noanswer"))

cfl$condition <- as.character(cfl$condition)
cfl$condition[cfl$condition == "Prefer not to answer"] <- NA
cfl$condition[cfl$condition == "control"] <- "Control"
cfl$condition[cfl$condition == "cfloss"] <- "CF Loss"
cfl$condition <- as.factor(cfl$condition)
cfl$condition <- factor(cfl$condition, ordered = TRUE, levels = c("Control", "CF Loss"))

# Calculating prevention, promotion, assessment, and locomotion scores
cfl$prev <- ((6-cfl$rfq_2) + (6-cfl$rfq_4) + cfl$rfq_5 + (6-cfl$rfq_6) + (6-cfl$rfq_8))/5
cfl$prom <- ((6-cfl$rfq_1) + cfl$rfq_3 + cfl$rfq_7 + (6-cfl$rfq_9) + cfl$rfq_10 + (6-cfl$rfq_11))/6
cfl$ass <- ((7-cfl$rmq_2) + cfl$rmq_6 + cfl$rmq_7 + cfl$rmq_9 + (7-cfl$rmq_10) + cfl$rmq_11 + cfl$rmq_15 + cfl$rmq_19 + cfl$rmq_20 + cfl$rmq_22 + (7-cfl$rmq_27) + cfl$rmq_30)/12
cfl$loc <- (cfl$rmq_1 + cfl$rmq_3 + cfl$rmq_4 + cfl$rmq_5 + cfl$rmq_8 + cfl$rmq_16 + cfl$rmq_21 + cfl$rmq_25 + cfl$rmq_28 + cfl$rmq_29 + (7-cfl$rmq_13) + (7-cfl$rmq_24))/12

# Calculating SD within prevention, promotion, assessment, and locomotion scores
cfl$rfq_2r <- 6-cfl$rfq_2
cfl$rfq_4r <- 6-cfl$rfq_4
cfl$rfq_6r <- 6-cfl$rfq_6
cfl$rfq_8r <- 6-cfl$rfq_8
cfl$rfq_1r <- 6-cfl$rfq_1
cfl$rfq_9r <- 6-cfl$rfq_9
cfl$rfq_11r <- 6-cfl$rfq_11
cfl$rmq_2r <- 7-cfl$rmq_2
cfl$rmq_10r <- 7-cfl$rmq_10
cfl$rmq_27r <- 7-cfl$rmq_27
cfl$rmq_13r <- 7-cfl$rmq_13
cfl$rmq_24r <- 7-cfl$rmq_24
cfl$prev.var <- apply(cfl[, c("rfq_2r","rfq_4r","rfq_5","rfq_6r","rfq_8r")], 1, var)
cfl$prom.var <- apply(cfl[, c("rfq_1r","rfq_3","rfq_7","rfq_9r","rfq_10","rfq_11r")], 1, var)
cfl$ass.var <- apply(cfl[,
                        c("rmq_2r","rmq_6","rmq_7","rmq_9","rmq_10r","rmq_11",
                          "rmq_15","rmq_19","rmq_20","rmq_22","rmq_27r","rmq_30")], 1, var)
cfl$loc.var <- apply(cfl[,
                        c("rmq_1","rmq_3","rmq_4","rmq_5","rmq_8","rmq_16",
                          "rmq_21","rmq_25","rmq_28","rmq_29","rmq_13r","rmq_24r")], 1, var)

# Calculating prevention dominance scores and mean-centering them
cfl$prevdom <- cfl$prev - cfl$prom
cfl$prevdomc <- cfl$prevdom
cfl$prevdomc <- scale(cfl$prevdomc, center = TRUE, scale = FALSE)

# Calculating mean-centered prevention, promotion, assessment, and locomotion scores
cfl$premc <- cfl$prev
cfl$premc <- as.numeric(scale(cfl$premc, center = TRUE, scale = FALSE))
cfl$promc <- cfl$prom
cfl$promc <- as.numeric(scale(cfl$promc, center = TRUE, scale = FALSE))
cfl$amc <- cfl$ass
cfl$amc <- as.numeric(scale(cfl$amc, center = TRUE, scale = FALSE))
cfl$lmc <- cfl$loc
cfl$lmc <- as.numeric(scale(cfl$lmc, center = TRUE, scale = FALSE))

# Standardizing scores for potential mediators
cfl$perfaffected.s <- cfl$perfaffected
cfl$perfaffected.s <- scale(cfl$perfaffected.s)
cfl$missedout.s <- cfl$missedout
cfl$missedout.s <- scale(cfl$missedout.s)
cfl$regret.s <- cfl$regret
cfl$regret.s <- scale(cfl$regret.s)
cfl$investearlier.s <- cfl$investearlier
cfl$investearlier.s <- scale(cfl$investearlier.s)
cfl$happier.s <- cfl$happier
cfl$happier.s <- scale(cfl$happier.s)
cfl$relieved.s <- cfl$relieved
cfl$relieved.s <- scale(cfl$relieved.s)

# Creating dummy variables for high/low median splits by prevention, promotion, assesment, and locomotion
cfl$hiloprev <- ifelse(cfl$prev > median(cfl$prev, na.rm=TRUE),"hiprev","loprev")
cfl$hiloprom <- ifelse(cfl$prom > median(cfl$prom, na.rm=TRUE),"hiprom","loprom")
cfl$hiloass <- ifelse(cfl$ass > median(cfl$ass, na.rm=TRUE),"hiass","loass")
cfl$hiloloc <- ifelse(cfl$loc > median(cfl$loc, na.rm=TRUE),"hiloc","loloc")

# Dummy-coding experimental condition variable (for regression):
cfl$condD[cfl$condition == "CF Loss"] <- 1
cfl$condD[cfl$condition == "Control"] <- 0

# Standardizing variables of interest for mediation analyses:
cfl$premc.s <- scale(cfl$premc)
cfl$promc.s <- scale(cfl$promc)
cfl$allo.s <- scale(cfl$allo)
cfl$prevdomc.s <- scale(cfl$prevdomc)

# Effect-coding experimental condition variable (for mediation analyses):
cfl$condE[cfl$condition == "CF Loss"] <- 1
cfl$condE[cfl$condition == "Control"] <- -1
```

```{r save.coded, echo=FALSE, include = FALSE}
# SAVING CODED DATASETS
cflorig <- cfl

# Overall
save(cflorig, file = "data/rfcfloss_coded.RData")
```

# Participants

## Exclusions

### Excluding participants who did not complete our IV and/or DV

```{r ivdv.excl, include = FALSE}
# Excluding those missing Bitcoin allocation (DV)
cflorig.alloexcl <- cflorig[ which(is.na(cflorig$allo) == FALSE ) , ]

# Excluding those missing prevention (one of two IVs)
cflorig.prevexcl <- cflorig.alloexcl[ which(is.na(cflorig.alloexcl$prev) == FALSE ) , ]

cflorig.ivdvexcl.n <- 500 - nrow(cflorig.prevexcl)
```

As per our pre-defined exclusion criteria, `r cflorig.ivdvexcl.n` participants were excluded for not submitting a Bitcoin allocation percentage (our dependent measure) or completing the Regulatory Focus Questionnaire ("RFQ"), which was used to calculate chronic prevention pride scores (one of our two independent measures).

### Deciding whether to exclude participants with fraudulent IP addresses

Soon after running this study, it became clear that data quality issues had recently surfaced on M-Turk due to foreign workers masking their location through Virtual Private Servers [see, for example, @dennisetal2018; @kennedyetal2018]. As a result, although not specified in our preregistration, we decided to consider excluding participants for data quality issues resulting from fraudulent IP addresses based on an investigation of the reliability of these responses.

```{r ip, include = FALSE}
cflexcl <- cflorig.prevexcl
# blockornot <- getIPinfo(cflexcl1, "IPAddress", "[key]")
# Anyone looking to rerun the line of code above will need to secure a free X-key
# from iphub.info and place it within the quotes

# blockornot <- rename(blockornot, IPAddress = ip)
cflexcl <- merge(cflexcl, blockornot, by = "IPAddress") # Merging blockornot results

## Determining participants flagged as block = (1 or 2) vs. 1 only
cflexcl$block12 <- ifelse(cflexcl$block == "0", 0, 1)
cflexcl$block <- as.numeric(cflexcl$block)
cflexcl$block.d <- ifelse(cflexcl$block == 1, 1, 0)

blocked1s <- nrow(subset(cflexcl, block.d == 1)) # 147 1's
blocked12s <- nrow(subset(cflexcl, block12 == 1)) # 151 1's and 2's
```

We examined our dataset for fraudulent responses based on users' IP addresses using `r cite_r("manuscript/rfcfloss.bib", pkgs = c("rIP"), withhold = FALSE)`. This package returns the dataset with a "block" column including a coded score indicating if the IP address is likely from a server farm and warrants exclusion. In doing so, we discovered `r blocked1s` participants who met this criterion and received an *rIP* "block" score of 1. (We selected the less stringent of the two "block" scores within the *rIP* package to minimize exclusions, but the following findings are consistent regardless of which "block" score was used.) We then probed these purportedly fraudulent responses to determine if their quality differed substantially from the rest of our sample.

```{r iptest.alpha, include = FALSE}
# Cronbach alpha when blocking 1s only
cflexcl.a <- select(cflexcl, rfq_2r, rfq_4r, rfq_5, rfq_6r, rfq_8r, block.d)
cflexcl.a.noblock <- subset(cflexcl.a, block.d == 0) # n = 334
cflexcl.a.noblock$block.d <- NULL # Removing column so I can calculate Cronbach's alpha below
cflexcl.a.block <- subset(cflexcl.a, block.d == 1) # n = 147
cflexcl.a.block$block.d <- NULL # Removing column so I can calculate Cronbach's alpha below

a.noblock <- psych::alpha(cflexcl.a.noblock)$total$std.alpha # Cronbach's alpha of unblocked group = 0.86
a.block <- psych::alpha(cflexcl.a.block)$total$std.alpha # Cronbach's alpha of blocked group = 0.55
feldttest <- cocron.two.coefficients(alpha = c(a.noblock,a.block), n = c(nrow(cflexcl.a.noblock),nrow(cflexcl.a.block)), dep = FALSE, alternative = "two.sided") # Significantly lower Cronbach's alpha in blocked group (p < .001)
```

First, we examined internal reliability. In previous research, Higgins and colleagues [-@higginsetal2001] found that the reliability of the prevention scale was 0.80, and among participants who did *not* receive a block score of 1, the Cronbach's alpha of the prevention items was in line with this estimate ($\alpha = `r myround(a.noblock, digits = 2)`$). However, among the responses who received a block score of 1 (thus indicating fraudulence), the Cronbach's alpha of the prevention items was `r myround(a.block, digits = 2)`. In particular, this reduced reliability appeared to be driven by reverse-coded items, as among this group, the function produced a warning message prompting us to confirm that the reverse-coded items were coded correctly (which we confirmed). To be clear, participants flagged as fraudulent did not respond to reverse-coded items as if they were reverse-coded, whereas other participants did. Following a method by Feldt et al. [-@feldtetal1987] to determine the equality of two Cronbach's alphas in which the statistic *W* is distributed as *F*, we also used the R-package *cocron* [Version 1.0.1; @R-cocron] to perform a statistical comparison of these two reliabilities. We found that the chronic prevention pride scores among participants flagged as fraudulent were significantly less reliable than non-flagged participants' scores, $W(`r feldttest@df[1]`, `r feldttest@df[2]`) = `r myround(feldttest@statistic, digits = 2)`, p < .001$.

```{r iptest.var, include = FALSE}
# Variance when blocking 1s only
varblocked <- mean(cflexcl$prev.var[cflexcl$block == 1], na.rm = TRUE) # average prev var = 0.951
varunblocked <- mean(cflexcl$prev.var[cflexcl$block != 1], na.rm = TRUE) # average prev var = 0.609
```

```{r iptest.var.test, include = FALSE}
vartest <- t.test(prev.var ~ block.d, data = cflexcl)
```

```{r iptest.var.output, include = FALSE}
cflexcl.blocked <- cflexcl[cflexcl$block.d == 0,] # Blocking flagged as "1"; n = 334
cflexcl.blocked.usonly <- cflexcl.blocked[cflexcl.blocked$countryCode == "US",] # n = 301
cfl.ipexcl <- cflexcl.blocked.usonly
cfl <- cflexcl.blocked.usonly
cfl.postip <- nrow(cfl)
cfl.excludedbyip <- nrow(cflexcl) - cfl.postip
```

Additionally, we examined the variance of responses to prevention-specific items from the RFQ. The variance across prevention items in the RFQ was also significantly greater among participants in the potentially fraudulent group (`r myround(varblocked, digits = 2)`) than among the non-flagged participant group (`r myround(varunblocked, digits = 2)`), $t(`r myround(vartest[["parameter"]], digits = 2)`) = `r myround(vartest[["statistic"]], digits = 2)`, p < .001$.

As a result, we excluded all participants with a "block" score of 1. (We selected the less stringent of the two "block" scores within the package to minimize exclusions, but the following findings are consistent regardless of which "block" score was used.) We also excluded all participants whose IP addresses revealed they were not located in the United States, which was required for all participants.

### Deciding whether to exclude participants who had not previously invested in Bitcoin

Among the remaining participants, we noted in our preregistration that if less than 10% of our sample comprises participants who report previously investing in Bitcoin, then we would exclude all participants who previously invested in Bitcoin (as this group might be expected to respond differently to our experimental manipulation); if 10% or more of our data is made of participants who previously invested in Bitcoin, then we will also conduct our analyses both including and excluding those participants, and will report any differences that emerge.

```{r subset1, include=FALSE}
cfl.noprevinv <- subset(cfl, previnvested != 1)
cfl.noprevinv.pct <- myround((nrow(cfl.ipexcl)-nrow(cfl.noprevinv))/nrow(cfl.ipexcl) * 100, digits = 2)
```

`r cfl.noprevinv.pct`% previously invested in Bitcoin (more than 10%), so we *did not* proceed with exclusion.

### Deciding whether to exclude those who learned about the study from other participants

Similarly, we noted in our preregistration that if less than 10% of our sample is composed of participants who report being told details about the beta-test or the DigiVest platform from another participant, then we will exclude these participants. 

```{r subset2, include=FALSE}
cfl.didntlearn <- subset(cfl, told_test != 1)
cfl.didntlearn.pct <- myround((nrow(cfl.ipexcl)-nrow(cfl.didntlearn))/nrow(cfl.ipexcl) * 100, digits = 2)
```

Only `r cfl.didntlearn.pct`% of our sample reported learning about the study from other participants (less than 10%), so we *did* proceed with exclusion. As described in our preregistration, we also reran our primary analyses without this exclusion to confirm that our findings were consistent (see final section of this Supplementary Materials document).

### Redefining dataset to reflect exclusions (per pre-registration; to be edited if either excluded group is >10%)

```{r subset3, include=FALSE}
# cfl <- subset(cfl, previnvested != 1) NOT EXCLUDED BECAUSE >10%
cfl.rerun <- cfl.ipexcl # n = 301
cfl <- subset(cfl, told_test != 1) # n = 295
```

```{r n, include = FALSE}
n <- length(unique(cfl$ResponseId))
```

These exclusions left us with a final sample size of `r n`.

```{r anonymous, include=FALSE}
## Removing unnecessary columns from cleaned data so it can be shared without compromising participants' anonymity
cfl$IPAddress <- NULL
cfl$Status <- NULL
cfl$RecipientFirstName <- NULL
cfl$RecipientLastName <- NULL
cfl$RecipientEmail <- NULL
cfl$LocationLatitude <- NULL
cfl$LocationLongitude <- NULL
cfl$ExternalReference <- NULL
cfl$DistributionChannel <- NULL
cfl$welcome <- NULL
cfl$MTurkCode <- NULL
cfl$RecordedDate <- NULL
```

```{r subset4, include=FALSE}
## Creating subset to facilitate visualization of results within each condition
cfl.cflcond <- subset(cfl, condition == "CF Loss") # n = 142
cfl.ctrlcond <- subset(cfl, condition == "Control") # n = 153
```

```{r save, include = FALSE}
## Saving cleaned dataframes
save(cfl, blockornot, cflorig, cflexcl1, cflexcl, cfl.cflcond, cfl.ctrlcond, file = "data/rfcfloss_clean.RData")
write.csv(cfl, file = "data/rfcfloss_clean.csv")
```

```{r age, include = FALSE}
## Calculating descriptive statistics for demographic variables
meanage <- mean(cfl$age, na.rm = TRUE)
sdage <- sd(cfl$age, na.rm = TRUE)
maxage <- max(cfl$age, na.rm = TRUE)
minage <- min(cfl$age, na.rm = TRUE)
```

```{r gender, include = FALSE}
male <- sum(cfl$gender == "male")
female <- sum(cfl$gender == "female")
malepct <- myround(male/nrow(cfl)*100, digits = 2)
femalepct <- myround(female/nrow(cfl)*100, digits = 2)
```

```{r language, include = FALSE}
english <- sum(cfl$language == "english")
engpct <- myround(english/nrow(cfl)*100, digits = 2)
```

```{r ethnicity, include = FALSE}
white <- sum(cfl$ethnicity == "white")
whitepct <- myround(white/nrow(cfl)*100, digits = 2)
hisp <- sum(cfl$ethnicity == "hispanic")
hisppct <- myround(hisp/nrow(cfl)*100, digits = 2)
black <- sum(cfl$ethnicity == "black")
blackpct <- myround(black/nrow(cfl)*100, digits = 2)
asian <- sum(cfl$ethnicity == "asian")
asianpct <- myround(asian/nrow(cfl)*100, digits = 2)
```

```{r income, include = FALSE}
cfl$income[is.na(cfl$income)] <- "noanswer"
tentwenty <- sum(cfl$income == "$10K-$20K")
tentwentypct <- myround(tentwenty/nrow(cfl)*100, digits = 2)
twentyforty <- sum(cfl$income == "$20K-$40K")
twentyfortypct <- myround(twentyforty/nrow(cfl)*100, digits = 2)
fortyseventy <- sum(cfl$income == "$40K-$70K")
fortyseventypct <- myround(fortyseventy/nrow(cfl)*100, digits = 2)
seventyhundred <- sum(cfl$income == "$70K-$100K")
seventyhundredpct <- myround(seventyhundred/nrow(cfl)*100, digits = 2)
hundredtwofifty <- sum(cfl$income == "$100K-$250K")
hundredtwofiftypct <- myround(hundredtwofifty/nrow(cfl)*100, digits = 2)
twofiftyfive <- sum(cfl$income == "$250K-$500K")
twofiftyfivepct <- myround(twofiftyfive/nrow(cfl)*100, digits = 2)
fiveplus <- sum(cfl$income == "$500K+")
fivepluspct <- myround(fiveplus/nrow(cfl)*100, digits = 2)
cfl$income[cfl$income == "noanswer"] <- NA
```

```{r edu, include = FALSE}
cfl$education[is.na(cfl$education)] <- "noanswer"
elementary <- sum(cfl$education == "elementary")
elementarypct <- myround(elementary/nrow(cfl)*100, digits = 2)
somehs <- sum(cfl$education == "somehs")
somehspct <- myround(somehs/nrow(cfl)*100, digits = 2)
highschool <- sum(cfl$education == "highschool")
highschoolpct <- myround(highschool/nrow(cfl)*100, digits = 2)
somecollege <- sum(cfl$education == "somecollege")
somecollegepct <- myround(somecollege/nrow(cfl)*100, digits = 2)
associates <- sum(cfl$education == "associates")
associatespct <- myround(associates/nrow(cfl)*100, digits = 2)
bachelors <- sum(cfl$education == "bachelors")
bachelorspct <- myround(bachelors/nrow(cfl)*100, digits = 2)
graddegree <- sum(cfl$education == "graddegree")
graddegreepct <- myround(graddegree/nrow(cfl)*100, digits = 2)
doctorate <- sum(cfl$education == "doctorate")
doctoratepct <- myround(doctorate/nrow(cfl)*100, digits = 2)
cfl$education[cfl$education == "noanswer"] <- NA
```

## Final Sample

Our final dataset includes observations from these `r n` M-Turk participants. The sample had a mean age of `r myround(meanage, digits = 2)` years ($SD = `r myround(sdage, digits = 2)`$, ranging from `r minage` to `r maxage`) and were `r malepct`% male and `r femalepct`% female. `r engpct`% of participants ($n = `r english`$) reported English as their native language. The ethnic breakdown in order of size was white ($n = `r white`$, `r whitepct`%), black ($n = `r black`$, `r blackpct`%), Asian ($n = `r asian`$, `r asianpct`%), and Hispanic ($n = `r hisp`$, `r hisppct`%). The income breakdown in order of size was \$70K - \$100K ($n = `r seventyhundred`$, `r seventyhundredpct`%), \$40K - \$70K ($n = `r fortyseventy`$, `r fortyseventypct`%), \$100K - \$250K ($n = `r hundredtwofifty`$, `r hundredtwofiftypct`%), \$20K - \$40K ($n = `r twentyforty`$, `r twentyfortypct`%), \$250K - \$500K ($n = `r twofiftyfive`$, `r twofiftyfivepct`%), \$10K - \$20K ($n = `r tentwenty`$, `r tentwentypct`%), and \$500K+ ($n = `r fiveplus`$, `r fivepluspct`%). The highest level of education participants reported attaining in order of size was a graduate degree ($n = `r graddegree`$, `r graddegreepct`%), an associate's degree ($n = `r associates`$, `r associatespct`%), some college ($n = `r somecollege`$, `r somecollegepct`%), a bachelor's degree ($n = `r bachelors`$, `r bachelorspct`%), a doctorate ($n = `r doctorate`$, `r doctoratepct`%), and a high school diploma ($n = `r highschool`$, `r highschoolpct`%). Histogram plots for each of these demographic measures are included below.

# Descriptive Plots

## Participants

```{r desc.ps, echo = FALSE, warning = FALSE, message = FALSE}
# Plots
ggplot(data=cfl, aes(x = age)) +
  geom_histogram(bins = 10) +
  labs(title="Histogram of Participant Age", x="Age", y="Participants")

cfl$ethnicity.ord <- factor(cfl$ethnicity, ordered = TRUE, levels = c("white", "black", "asian", "multi", "hispanic"))
cfl$ethnicity.ord <- droplevels(cfl$ethnicity.ord)
ggplot(data=subset(cfl, !is.na(ethnicity.ord)), aes(x = ethnicity.ord)) +
  scale_x_discrete(labels = c("White", "Black", "Asian", "Multiracial", "Hispanic")) +
  geom_histogram(stat = "count") +
  labs(title="Histogram of Participant Ethnicity", x="Ethnicity", y="Participants")

ggplot(subset(cfl, !is.na(income)), aes(x = income)) +
  scale_x_discrete(labels = c("$10K-\n$20K", "$20K-\n$40K", "$40K-\n$70K", "$70K-\n$100K", "$100K-\n$250K", "$250K-\n$500K", "$500K+")) +
  geom_bar(stat = "count") +
  labs(title = "Histogram of Participant Income", x = "Income", y = "Participants")

ggplot(subset(cfl, !is.na(education)), aes(x = education)) +
  scale_x_discrete(labels = c("High\nSchool", "Some\nCollege", "Associate's\nDegree", "Bachelor's\nDegree", "Graduate\nDegree", "Doctorate")) +
  geom_bar(stat = "count") +
  labs(title = "Histogram of Participant Education", x = "Education", y = "Participants")
```

## Bitcoin Allocation by Prevention Pride and Condition

```{r desc, echo = FALSE, warning = FALSE, message = FALSE}
# summarySE() function defined at top of document
cflsummary <- summarySE(cfl, measurevar="allo", groupvars=c("hiloprev","condition"))

ggplot(data=cfl, aes(x = hiloprev, y = allo, color = hiloprev)) +
  facet_wrap(. ~ condition) +
  geom_jitter() +
  geom_errorbar(data = cflsummary, aes(ymin = allo - se, ymax = allo + se),
                     , col = "black", size = .5) +
  geom_point(data = cflsummary, col = "black", size = 3, alpha = 1) +
  scale_x_discrete(labels = c("High", "Low")) +
  labs(title="Bitcoin Allocation By Counterfactual Loss and Prevention Pride\n(NOTE: Does Not Control for Effects of Promotion Pride)", x="Prevention Pride (Median-Split)", y="Bitcoin Allocation (%)") +
  theme(legend.position = "none")

```

# Primary Linear Analyses

## Hypothesized Model

As described in the article, we were primarily interested in examining if participants' chronic prevention pride interacted with counterfactual loss to predict allocation of one's funds toward a risky investment in Bitcoin. To test our hypothesis, we entered these predictors into a linear regression analysis, the results of which are presented in Table 1. To supplement these results, a visualization of the model's predictions is presented in the following figure. Additionally, we built an application to dynamically generate model predictions using `r cite_r("manuscript/rfcfloss.bib", pkgs = "shiny", withhold = FALSE)`. The application is located online at http://regfocusrisk.com ([Anonymous], 2019).

```{r primarymodel, include = FALSE}
rfcfl.promctr.nonstd <- lm(allo ~ premc * condD + promc * condD, data = cfl)
```

```{r primarymodeltable, include = FALSE}
table1 <- tidy(rfcfl.promctr.nonstd)
table1 <- dplyr::rename(table1, Predictor = term, Estimate = estimate, SE = std.error, t = statistic, p = p.value)
table1$Estimate <- myround(table1$Estimate, digits = 2)
table1$SE <- myround(table1$SE, digits = 2)
table1$t <- myround(table1$t, digits = 2)
table1$p <- myround(table1$p, digits = 3)
table1$p[table1$p < .001] <- "< .001"
table1$Predictor[table1$Predictor == "(Intercept)"] <- "Intercept"
table1$Predictor[table1$Predictor == "premc"] <- "Prevention Pride"
table1$Predictor[table1$Predictor == "condD"] <- "Counterfactual Loss"
table1$Predictor[table1$Predictor == "promc"] <- "Promotion Pride"
table1$Predictor[table1$Predictor == "premc:condD"] <- "Prevention Pride x Counterfactual Loss"
table1$Predictor[table1$Predictor == "condD:promc"] <- "Promotion Pride x Counterfactual Loss"
table1[is.na(table1)] <- ""
table1$order <- c(1, 2, 3, 5, 4, 6)
table1 <- arrange(table1, order)
table1$order <- NULL

df <- rfcfl.promctr.nonstd$df.residual
```

```{r primarymodelprint, echo = FALSE, include = TRUE, results = 'asis'}
apa_table(table1, caption = "Summary of Linear Regression Analysis", note = "This analysis included a dummy-coded variable for the counterfactual loss manipulation: 0 = control, 1 = counterfactual loss. Additionally, prevention and promotion pride were mean-centered within this model. Estimated effect sizes reported here are unstandardized regression coefficients.", align = 'lrrrr')
```

```{r primarymodelplot_generate, echo = FALSE, include = FALSE}
pred.data.ctrl <- data.frame(premc = seq(min(cfl$premc, na.rm=T), 
                                         max(cfl$premc, na.rm=T), .1),
                                         promc = 0, condD = 0, condition = "Control")
rfcfl.promctr.pred.ctrl <- cbind(pred.data.ctrl, 
                                 predict(rfcfl.promctr.nonstd, pred.data.ctrl, 
                                         interval = "confidence", 
                                         type = c("response", "terms")))
rfcfl.promctr.pred.ctrl <- dplyr::rename(rfcfl.promctr.pred.ctrl, allo = fit)

pred.data.CFL <- data.frame(premc = seq(min(cfl$premc, na.rm=T), 
                                        max(cfl$premc, na.rm=T), .1),
                                        promc = 0, condD = 1, condition = "CF Loss")
rfcfl.promctr.pred.CFL <- cbind(pred.data.CFL, 
                                predict(rfcfl.promctr.nonstd, pred.data.CFL, 
                                        interval = "confidence", 
                                        type = c("response", "terms")))
rfcfl.promctr.pred.CFL <- dplyr::rename(rfcfl.promctr.pred.CFL, allo = fit)

primarymodel <- ggplot(data=cfl, aes(x=premc, y=allo)) +
       scale_color_manual(values=c("gray0", "gray50")) +
       geom_ribbon(data = rfcfl.promctr.pred.ctrl, aes(ymin = lwr, ymax = upr), alpha = .3, fill = "gray") +
       geom_ribbon(data = rfcfl.promctr.pred.CFL, aes(ymin = lwr, ymax = upr), alpha = .3, fill = "gray") +
       geom_line(data = rfcfl.promctr.pred.ctrl, aes(color=condition), size = 1) +
       geom_line(data = rfcfl.promctr.pred.CFL, aes(color=condition), size = 1) +
       labs(title="Prevention Pride and Counterfactual Loss as\nPredictors of Bitcoin Allocation\n(Controlling for Promotion Pride and the Interaction\nBetween Promotion Pride and Counterfactual Loss)", x="Prevention Pride (Mean-Centered)", y="Bitcoin Allocation (%)", color = "Condition")
```

```{r primarymodelplot, echo = FALSE, include = TRUE, fig.cap = "Predicted Bitcoin allocation by prevention pride and counterfactual loss experience, controlling for promotion pride and the interaction between promotion pride and counterfactual loss.", fig.align = "center", out.width = '90%', out.height = '90%'}
primarymodel
```

The results revealed no main effects of any single predictor. However, as predicted, the analysis yielded a significant two-way interaction between prevention pride and counterfactual loss condition ($B = `r myround(as.numeric(table1[4,"Estimate"]), digits = 2)`, t(`r df`) = `r myround(as.numeric(table1[4,"t"]), digits = 2)`, `r pval(as.numeric(table1[4,"p"]))`$).

## Hypothesized Model Without Promotion Pride and With Demographic Covariates

```{r primarymodel.nopromctr, include = FALSE}
# Not controlling for promotion pride or interaction between promotion pride and CF Loss (mean-centered RF and dummy-coded condition)
rfcfl <- lm(allo ~ premc * condD, data=cfl)
table1.noprom <- tidy(rfcfl)
table1.noprom <- dplyr::rename(table1.noprom, Predictor = term, Estimate = estimate, SE = std.error, t = statistic, p = p.value)
table1.noprom$Estimate <- myround(table1.noprom$Estimate, digits = 2)
table1.noprom$p <- myround(table1.noprom$p, digits = 3)
table1.noprom$p[table1.noprom$p < .001] <- "< .001"
table1.noprom$Predictor[table1.noprom$Predictor == "(Intercept)"] <- "Intercept"
table1.noprom$Predictor[table1.noprom$Predictor == "premc"] <- "Prevention Pride"
table1.noprom$Predictor[table1.noprom$Predictor == "condD"] <- "Counterfactual Loss"
table1.noprom$Predictor[table1.noprom$Predictor == "premc:condD"] <- "Prevention Pride x Counterfactual Loss"
table1.noprom[is.na(table1.noprom)] <- ""
```

```{r primarymodel.promctrnointxn, include = FALSE}
# Not controlling for promotion pride (mean-centered RF and dummy-coded condition)
rfcfl.promctrnointxn <- lm(allo ~ premc * condD + promc, data=cfl)
table1.promctrnointxn <- tidy(rfcfl.promctrnointxn)
table1.promctrnointxn <- dplyr::rename(table1.promctrnointxn, Predictor = term, Estimate = estimate, SE = std.error, t = statistic, p = p.value)
table1.promctrnointxn$Estimate <- myround(table1.promctrnointxn$Estimate, digits = 2)
table1.promctrnointxn$p <- myround(table1.promctrnointxn$p, digits = 3)
table1.promctrnointxn$p[table1.promctrnointxn$p < .001] <- "< .001"
table1.promctrnointxn$Predictor[table1.promctrnointxn$Predictor == "(Intercept)"] <- "Intercept"
table1.promctrnointxn$Predictor[table1.promctrnointxn$Predictor == "premc"] <- "Prevention Pride"
table1.promctrnointxn$Predictor[table1.promctrnointxn$Predictor == "condD"] <- "Counterfactual Loss"
table1.promctrnointxn$Predictor[table1.promctrnointxn$Predictor == "premc:condD"] <- "Prevention Pride x Counterfactual Loss"
table1.promctrnointxn$Predictor[table1.promctrnointxn$Predictor == "promc"] <- "Promotion Pride"
table1.promctrnointxn[is.na(table1.promctrnointxn)] <- ""
```

```{r covariates, echo = FALSE}
# Controlling for gender (mean-centered RF and dummy-coded condition)
rfcfl.promctr.gender <- lm(allo ~ premc * condD + gender + promc * condD, data=cfl)
table1.gender <- tidy(rfcfl.promctr.gender)
table1.gender <- dplyr::rename(table1.gender, Predictor = term, Estimate = estimate, SE = std.error, t = statistic, p = p.value)
table1.gender$Estimate <- myround(table1.gender$Estimate, digits = 2)
table1.gender$p <- myround(table1.gender$p, digits = 3)
table1.gender$p[table1.gender$p < .001] <- "< .001"
table1.gender$Predictor[table1.gender$Predictor == "(Intercept)"] <- "Intercept"
table1.gender$Predictor[table1.gender$Predictor == "premc"] <- "Prevention Pride"
table1.gender$Predictor[table1.gender$Predictor == "condD"] <- "Counterfactual Loss"
table1.gender$Predictor[table1.gender$Predictor == "promc"] <- "Promotion Pride"
table1.gender$Predictor[table1.gender$Predictor == "gendermale"] <- "Gender: Male"
table1.gender$Predictor[table1.gender$Predictor == "genderfemale"] <- "Gender: Female"
table1.gender$Predictor[table1.gender$Predictor == "premc:condD"] <- "Prevention Pride x Counterfactual Loss"
table1.gender$Predictor[table1.gender$Predictor == "condD:promc"] <- "Promotion Pride x Counterfactual Loss"
table1.gender[is.na(table1.gender)] <- ""

# Controlling for age (mean-centered RF and dummy-coded condition)
rfcfl.promctr.age <- lm(allo ~ premc * condD + age + promc * condD, data=cfl)
table1.age <- tidy(rfcfl.promctr.age)
table1.age <- dplyr::rename(table1.age, Predictor = term, Estimate = estimate, SE = std.error, t = statistic, p = p.value)
table1.age$Estimate <- myround(table1.age$Estimate, digits = 2)
table1.age$p <- myround(table1.age$p, digits = 3)
table1.age$p[table1.age$p < .001] <- "< .001"
table1.age$Predictor[table1.age$Predictor == "(Intercept)"] <- "Intercept"
table1.age$Predictor[table1.age$Predictor == "premc"] <- "Prevention Pride"
table1.age$Predictor[table1.age$Predictor == "condD"] <- "Counterfactual Loss"
table1.age$Predictor[table1.age$Predictor == "promc"] <- "Promotion Pride"
table1.age$Predictor[table1.age$Predictor == "age"] <- "Age"
table1.age$Predictor[table1.age$Predictor == "premc:condD"] <- "Prevention Pride x Counterfactual Loss"
table1.age$Predictor[table1.age$Predictor == "condD:promc"] <- "Promotion Pride x Counterfactual Loss"
table1.age[is.na(table1.age)] <- ""

# Controlling for ethnicity (mean-centered RF and dummy-coded condition)
rfcfl.promctr.ethnicity <- lm(allo ~ premc * condD + ethnicity + promc * condD, data=cfl)
table1.ethnicity <- tidy(rfcfl.promctr.ethnicity)
table1.ethnicity <- dplyr::rename(table1.ethnicity, Predictor = term, Estimate = estimate, SE = std.error, t = statistic, p = p.value)
table1.ethnicity$Estimate <- myround(table1.ethnicity$Estimate, digits = 2)
table1.ethnicity$p <- myround(table1.ethnicity$p, digits = 3)
table1.ethnicity$p[table1.ethnicity$p < .001] <- "< .001"
table1.ethnicity$Predictor[table1.ethnicity$Predictor == "(Intercept)"] <- "Intercept"
table1.ethnicity$Predictor[table1.ethnicity$Predictor == "premc"] <- "Prevention Pride"
table1.ethnicity$Predictor[table1.ethnicity$Predictor == "condD"] <- "Counterfactual Loss"
table1.ethnicity$Predictor[table1.ethnicity$Predictor == "promc"] <- "Promotion Pride"
table1.ethnicity$Predictor[table1.ethnicity$Predictor == "ethnicityasian"] <- "Ethnicity: Asian"
table1.ethnicity$Predictor[table1.ethnicity$Predictor == "ethnicityblack"] <- "Ethnicity: Black"
table1.ethnicity$Predictor[table1.ethnicity$Predictor == "ethnicityhispanic"] <- "Ethnicity: Hispanic"
table1.ethnicity$Predictor[table1.ethnicity$Predictor == "ethnicitymulti"] <- "Ethnicity: Multiracial"
table1.ethnicity$Predictor[table1.ethnicity$Predictor == "ethnicityother"] <- "Ethnicity: Other"
table1.ethnicity$Predictor[table1.ethnicity$Predictor == "ethnicitypacislander"] <- "Ethnicity: Pacific Islander"
table1.ethnicity$Predictor[table1.ethnicity$Predictor == "ethnicitywhite"] <- "Ethnicity: White"
table1.ethnicity$Predictor[table1.ethnicity$Predictor == "premc:condD"] <- "Prevention Pride x Counterfactual Loss"
table1.ethnicity$Predictor[table1.ethnicity$Predictor == "condD:promc"] <- "Promotion Pride x Counterfactual Loss"
table1.ethnicity[is.na(table1.ethnicity)] <- ""

# Controlling for income (mean-centered RF and dummy-coded condition)
cfl$income.unord <- factor(cfl$income, ordered = F)
rfcfl.promctr.income <- lm(allo ~ premc * condD + income.unord + promc * condD, data=cfl)
table1.income <- tidy(rfcfl.promctr.income)
table1.income <- dplyr::rename(table1.income, Predictor = term, Estimate = estimate, SE = std.error, t = statistic, p = p.value)
table1.income$Estimate <- myround(table1.income$Estimate, digits = 2)
table1.income$p <- myround(table1.income$p, digits = 3)
table1.income$p[table1.income$p < .001] <- "< .001"
table1.income$Predictor[table1.income$Predictor == "(Intercept)"] <- "Intercept"
table1.income$Predictor[table1.income$Predictor == "premc"] <- "Prevention Pride"
table1.income$Predictor[table1.income$Predictor == "condD"] <- "Counterfactual Loss"
table1.income$Predictor[table1.income$Predictor == "promc"] <- "Promotion Pride"
table1.income$Predictor[table1.income$Predictor == "income.unord$20K-$40K"] <- "Income: $20K-$40K"
table1.income$Predictor[table1.income$Predictor == "income.unord$40K-$70K"] <- "Income: $40K-$70K"
table1.income$Predictor[table1.income$Predictor == "income.unord$70K-$100K"] <- "Income: $70K-$100K"
table1.income$Predictor[table1.income$Predictor == "income.unord$100K-$250K"] <- "Income: $100K-$250K"
table1.income$Predictor[table1.income$Predictor == "income.unord$250K-$500K"] <- "Income: $250K-$500K"
table1.income$Predictor[table1.income$Predictor == "income.unord$500K+"] <- "Income: $500K+"
table1.income$Predictor[table1.income$Predictor == "premc:condD"] <- "Prevention Pride x Counterfactual Loss"
table1.income$Predictor[table1.income$Predictor == "condD:promc"] <- "Promotion Pride x Counterfactual Loss"
table1.income[is.na(table1.income)] <- ""

# Controlling for education (mean-centered RF and dummy-coded condition)
cfl$edu.unord <- factor(cfl$edu, ordered = F)
rfcfl.promctr.edu <- lm(allo ~ premc * condD + edu.unord + promc * condD, data=cfl)
table1.edu <- tidy(rfcfl.promctr.edu)
table1.edu <- dplyr::rename(table1.edu, Predictor = term, Estimate = estimate, SE = std.error, t = statistic, p = p.value)
table1.edu$Estimate <- myround(table1.edu$Estimate, digits = 2)
table1.edu$p <- myround(table1.edu$p, digits = 3)
table1.edu$p[table1.edu$p < .001] <- "< .001"
table1.edu$Predictor[table1.edu$Predictor == "(Intercept)"] <- "Intercept"
table1.edu$Predictor[table1.edu$Predictor == "premc"] <- "Prevention Pride"
table1.edu$Predictor[table1.edu$Predictor == "condD"] <- "Counterfactual Loss"
table1.edu$Predictor[table1.edu$Predictor == "promc"] <- "Promotion Pride"
table1.edu$Predictor[table1.edu$Predictor == "edu.unordsomecollege"] <- "Education: Some College"
table1.edu$Predictor[table1.edu$Predictor == "edu.unordassociates"] <- "Education: Associate's"
table1.edu$Predictor[table1.edu$Predictor == "edu.unordbachelors"] <- "Education: Bachelor's"
table1.edu$Predictor[table1.edu$Predictor == "edu.unordgraddegree"] <- "Education: Grad. Degree"
table1.edu$Predictor[table1.edu$Predictor == "edu.unorddoctorate"] <- "Education: Doctorate"
table1.edu$Predictor[table1.edu$Predictor == "premc:condD"] <- "Prevention Pride x Counterfactual Loss"
table1.edu$Predictor[table1.edu$Predictor == "condD:promc"] <- "Promotion Pride x Counterfactual Loss"
table1.edu[is.na(table1.edu)] <- ""
```

As described in the article, the interaction between prevention pride and counterfactual loss remained significant when *not* including promotion pride in the model, as well as when controlling for a range of demographic variables. Tables 2-8 contain the results of these analyses.

```{r primarymodel.nopromctrprint, echo = FALSE, include = TRUE, results = 'asis'}
apa_table(table1.noprom, caption = "Summary of Linear Regression Analysis Not Controlling for Promotion Pride or the Interaction Between Promotion Pride and Counterfactual Loss", note = "This analysis included a dummy-coded variable for the counterfactual loss manipulation: 0 = control, 1 = counterfactual loss. Additionally, prevention pride was mean-centered within this model. Estimated effect sizes reported here are unstandardized regression coefficients.", align = 'lrrrr')

apa_table(table1.promctrnointxn, caption = "Summary of Linear Regression Analysis Not Controlling for the Interaction Between Promotion Pride and Counterfactual Loss", note = "This analysis included a dummy-coded variable for the counterfactual loss manipulation: 0 = control, 1 = counterfactual loss. Additionally, prevention and promotion pride were mean-centered within this model. Estimated effect sizes reported here are unstandardized regression coefficients.", align = 'lrrrr')
```

```{r covariatesprint, echo = FALSE, include = TRUE, results = 'asis'}
apa_table(table1.gender, caption = "Summary of Linear Regression Analysis Controlling for Gender", note = "This analysis included a dummy-coded variable for the counterfactual loss manipulation: 0 = control, 1 = counterfactual loss. Additionally, prevention and promotion pride were mean-centered within this model. Estimated effect sizes reported here are unstandardized regression coefficients.", align = 'lrrrr')

apa_table(table1.age, caption = "Summary of Linear Regression Analysis Controlling for Age", note = "This analysis included a dummy-coded variable for the counterfactual loss manipulation: 0 = control, 1 = counterfactual loss. Additionally, prevention and promotion pride were mean-centered within this model. Estimated effect sizes reported here are unstandardized regression coefficients.", align = 'lrrrr')

apa_table(table1.ethnicity, caption = "Summary of Linear Regression Analysis Controlling for Ethnicity", note = "This analysis included a dummy-coded variable for the counterfactual loss manipulation: 0 = control, 1 = counterfactual loss. Additionally, prevention and promotion pride were mean-centered within this model. Estimated effect sizes reported here are unstandardized regression coefficients.", align = 'lrrrr')

apa_table(table1.income, caption = "Summary of Linear Regression Analysis Controlling for Income", note = "This analysis included a dummy-coded variable for the counterfactual loss manipulation: 0 = control, 1 = counterfactual loss. Additionally, prevention and promotion pride were mean-centered within this model. Estimated effect sizes reported here are unstandardized regression coefficients.", align = 'lrrrr')

apa_table(table1.edu, caption = "Summary of Linear Regression Analysis Controlling for Education", note = "This analysis included a dummy-coded variable for the counterfactual loss manipulation: 0 = control, 1 = counterfactual loss. Additionally, prevention and promotion pride were mean-centered within this model. Estimated effect sizes reported here are unstandardized regression coefficients.", align = 'lrrrr')
```

# Exploratory Mediation Analyses (Hayes PROCESS Model 8): Counterfactual Thought and Hypothetical Emotion Mediators

```{r cfthinking, include = FALSE}
missedoutmean <- round(mean(cfl$missedout, na.rm = TRUE), digits = 2)
missedoutsd <- round(sd(cfl$missedout, na.rm = TRUE), digits = 2)
regretmean <- round(mean(cfl$regret, na.rm = TRUE), digits = 2)
regretsd <- round(sd(cfl$regret, na.rm = TRUE), digits = 2)
investearliermean <- round(mean(cfl$investearlier, na.rm = TRUE), digits = 2)
investearliersd <- round(sd(cfl$investearlier, na.rm = TRUE), digits = 2)
happiermean <- round(mean(cfl$happier, na.rm = TRUE), digits = 2)
happiersd <- round(sd(cfl$happier, na.rm = TRUE), digits = 2)
relievedmean <- round(mean(cfl$relieved, na.rm = TRUE), digits = 2)
relievedsd <- round(sd(cfl$relieved, na.rm = TRUE), digits = 2)
```

As described in the article, in order to more clearly understand our hypothesized effect, we included a number of single-item measures examining the counterfactual thoughts that participants generated in the process of making their Bitcoin allocations. The results of all exploratory mediation analyses can be found in Tables 9-12.

## Exploratory Moderated Mediation Analysis: Missing Out

```{r med.missedout.promctr.lavaan, eval = FALSE, include = FALSE, warning = FALSE, message = FALSE, cache = TRUE}
# Specify model
Mod.Med.Lavaan.promctr.Missedout <- '
# Regressions
missedout.s ~ 1 + a1*premc.s + a2*condE + a3*premc.s:condE + a4*promc.s + a5*condE:promc.s
allo.s ~ 1 + cdash1*premc.s + cdash2*condE + b1*missedout.s + cdash3*premc.s:condE + cdash4*promc.s + cdash5*condE:promc.s

#Indirect effects conditional on moderator (a1 + a3*ModValue)*b1
indirect.ctrl := (a1 + a3*(-1))*b1
indirect.CFL := (a1 + a3*(1))*b1

#Direct effects conditional on moderator (cdash1 + cdash3*ModValue)
direct.ctrl := cdash1 + cdash3*(-1)
direct.CFL := cdash1 + cdash3*(1)

#Total effects conditional on moderator
total.ctrl := direct.ctrl + indirect.ctrl
total.CFL := direct.CFL + indirect.CFL

#Proportion mediated conditional on moderator
#To match the output of "mediate" package
prop.mediated.ctrl := indirect.ctrl / total.ctrl
prop.mediated.CFL := indirect.CFL / total.CFL

#Index of moderated mediation
#An alternative way of testing if conditional indirect effects are significantly different from each other
index.mod.med := a3*b1
'

# Fit model
set.seed(1234)
Mod.Med.SEM.promctr.missedout <- sem(model = Mod.Med.Lavaan.promctr.Missedout,
                                     data = cfl,
                                     se = "bootstrap",
                                     bootstrap = 5000)

summary(Mod.Med.SEM.promctr.missedout,
        fit.measures = FALSE,
        standardize = TRUE,
        estimates = TRUE,
        ci = TRUE,
        rsquare = TRUE)

save(Mod.Med.SEM.promctr.missedout, file = "models/missedoutPromctrFit.RData")
```

```{r med.missedout.promctr.lavaan.vis, include = FALSE, echo = FALSE, warning = FALSE, message = FALSE, cache = TRUE}
load("models/missedoutPromctrFit.RData")
summary(Mod.Med.SEM.promctr.missedout,
        fit.measures = FALSE,
        standardize = TRUE,
        estimates = TRUE,
        ci = TRUE,
        rsquare = TRUE)

missedoutPromctrCoefs <- parameterEstimates(Mod.Med.SEM.promctr.missedout)
a3.missedout.promctr <- missedoutPromctrCoefs$est[missedoutPromctrCoefs$label == "a3"]
a3.p.missedout.promctr <- missedoutPromctrCoefs$pvalue[missedoutPromctrCoefs$label == "a3"]
b.missedout.promctr <- missedoutPromctrCoefs$est[missedoutPromctrCoefs$label == "b1"]
b.p.missedout.promctr <- missedoutPromctrCoefs$pvalue[missedoutPromctrCoefs$label == "b1"]
condIndEffctrl.missedout.promctr <- missedoutPromctrCoefs$est[missedoutPromctrCoefs$label == "indirect.ctrl"]
condIndEffctrl.se.missedout.promctr <- missedoutPromctrCoefs$se[missedoutPromctrCoefs$label == "indirect.ctrl"]
condIndEffctrl.cilower.missedout.promctr <- missedoutPromctrCoefs$ci.lower[missedoutPromctrCoefs$label == "indirect.ctrl"]
condIndEffctrl.ciupper.missedout.promctr <- missedoutPromctrCoefs$ci.upper[missedoutPromctrCoefs$label == "indirect.ctrl"]
condIndEffCFL.missedout.promctr <- missedoutPromctrCoefs$est[missedoutPromctrCoefs$label == "indirect.CFL"]
condIndEffCFL.se.missedout.promctr <- missedoutPromctrCoefs$se[missedoutPromctrCoefs$label == "indirect.CFL"]
condIndEffCFL.cilower.missedout.promctr <- missedoutPromctrCoefs$ci.lower[missedoutPromctrCoefs$label == "indirect.CFL"]
condIndEffCFL.ciupper.missedout.promctr <- missedoutPromctrCoefs$ci.upper[missedoutPromctrCoefs$label == "indirect.CFL"]
```

```{r medmodel.missedout, include = FALSE}
table2.missedout <- missedoutPromctrCoefs 
table2.missedout <- dplyr::rename(table2.missedout, Predictor = rhs, Estimate = est, SE = se, p = pvalue, CI.lower = ci.lower, CI.upper = ci.upper)
table2.missedout$label <- NULL
table2.missedout <- table2.missedout[table2.missedout$op != "~~",]
table2.missedout$Predictor[table2.missedout$lhs == "missedout.s" & table2.missedout$op == "~1"] <- "Intercept"
table2.missedout$op[table2.missedout$lhs == "missedout.s" & table2.missedout$op == "~1"] <- "~"
table2.missedout$Predictor[table2.missedout$lhs == "allo.s" & table2.missedout$op == "~1"] <- "Intercept"
table2.missedout$op[table2.missedout$lhs == "allo.s" & table2.missedout$op == "~1"] <- "~"
table2.missedout <- table2.missedout[table2.missedout$op != "~1",]
table2.missedout <- table2.missedout[1:15,]
table2.missedout <- table2.missedout %>%
  mutate(section = recode(lhs, missedout.s = 1, allo.s = 2,
                          indirect.ctrl = 3, indirect.CFL = 4)) %>%
  arrange(section,desc(op))
table2.missedout$Predictor[table2.missedout$lhs == "indirect.ctrl"] <- "Control Condition"
table2.missedout$Predictor[table2.missedout$lhs == "indirect.CFL"] <- "Counterfactual Loss Condition"
table2.missedout$Estimate <- myround(table2.missedout$Estimate, digits = 2)
table2.missedout$SE <- myround(table2.missedout$SE, digits = 2)
table2.missedout$z <- myround(table2.missedout$z, digits = 2)
table2.missedout$p <- myround(table2.missedout$p, digits = 3)
table2.missedout$CI.lower <- myround(table2.missedout$CI.lower, digits = 4)
table2.missedout$CI.upper <- myround(table2.missedout$CI.upper, digits = 4)
table2.missedout$p[table2.missedout$p < .001] <- "< .001"
table2.missedout$Predictor[table2.missedout$Predictor == "premc.s"] <- "Prevention Pride"
table2.missedout$Predictor[table2.missedout$Predictor == "condE"] <- "Counterfactual Loss"
table2.missedout$Predictor[table2.missedout$Predictor == "promc.s"] <- "Promotion Pride"
table2.missedout$Predictor[table2.missedout$Predictor == "premc.s:condE"] <- "Prev. Pride x CF Loss"
table2.missedout$Predictor[table2.missedout$Predictor == "condE:promc.s"] <- "Prom. Pride x CF Loss"
table2.missedout$Predictor[table2.missedout$Predictor == "missedout.s"] <- "Missed Out"
table2.missedout[is.na(table2.missedout)] <- ""
table2.missedout$lhs <- NULL
table2.missedout$op <- NULL
table2.missedout$section <- NULL
table2.missedout$order <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 13, 10, 11, 12, 14, 15)
table2.missedout <- arrange(table2.missedout, order)
table2.missedout$order <- NULL

medmodel.missedout <- table2.missedout %>%
  mutate(
    Estimate = cell_spec(Estimate, "latex", align = "r"),
    SE = cell_spec(SE, "latex", align = "r"),
    z = cell_spec(z, "latex", align = "r"),
    p = cell_spec(p, "latex", align = "r"),
    CI.lower = cell_spec(CI.lower, "latex", align = "r"),
    CI.upper = cell_spec(CI.upper, "latex", align = "r")
  ) %>%
  kable("latex", booktabs = TRUE, escape = FALSE, caption = "Summary of Exploratory Mediation Analysis") %>%
  kable_styling(latex_options = c("scale_down")) %>%
  group_rows("Model 1 (DV = Missed Out)", 1, 6) %>%
  group_rows("Model 2 (DV = Bitcoin Allocation)", 7, 13) %>%
  group_rows("Bootstrapped Conditional Indirect Effects\n(Prev. Pride x CF Loss  Missed Out  Bitcoin Allocation)", 14, 15) %>%
  row_spec(0, align = "c") %>%
  footnote(general = "This analysis included an effect-coded variable for the counterfactual loss experience: -1 = control, 1 = counterfactual loss. Additionally, all other variables were standardized (M = 0, SD = 1) within this model. Estimated effect sizes for the models reported here are standardized regression coefficients.", general_title = "Note: ", footnote_as_chunk = T, title_format = c("italic"), threeparttable = TRUE, escape = FALSE)
```

```{r, echo = FALSE}
medmodel.missedout
```

When we control for promotion pride and the interaction between promotion and counterfactual loss, the interaction between prevention pride and counterfactual loss was only *marginally* associated with the degree to which participants reported they missed out by not investing in Bitcoin earlier ($\beta = `r myround(a3.missedout.promctr, digits = 2)`$, $p = `r myround(a3.p.missedout.promctr, digits = 3)`$), while the effect of participants reporting they missed out by not investing earlier ($\beta = `r myround(b.missedout.promctr, digits = 2)`$, $`r pval(as.numeric(b.p.missedout.promctr))`$) on Bitcoin allocation was significant. (See Table 9 for full model output.)

Given the marginal significance of the a path, we concluded that our interaction of interest is not mediated by missing out.

## Exploratory Moderated Mediation Analysis: Regret

```{r med.regret.promctr.lavaan, eval = FALSE, include = FALSE, warning = FALSE, message = FALSE, cache = TRUE}
# Specify model
Mod.Med.Lavaan.promctr.regret <- '
# Regressions
regret.s ~ 1 + a1*premc.s + a2*condE + a3*premc.s:condE + a4*promc.s + a5*condE:promc.s
allo.s ~ 1 + cdash1*premc.s + cdash2*condE + b1*regret.s + cdash3*premc.s:condE + cdash4*promc.s + cdash5*condE:promc.s

#Indirect effects conditional on moderator (a1 + a3*ModValue)*b1
indirect.ctrl := (a1 + a3*(-1))*b1
indirect.CFL := (a1 + a3*(1))*b1

#Direct effects conditional on moderator (cdash1 + cdash3*ModValue)
direct.ctrl := cdash1 + cdash3*(-1)
direct.CFL := cdash1 + cdash3*(1)

#Total effects conditional on moderator
total.ctrl := direct.ctrl + indirect.ctrl
total.CFL := direct.CFL + indirect.CFL

#Proportion mediated conditional on moderator
#To match the output of "mediate" package
prop.mediated.ctrl := indirect.ctrl / total.ctrl
prop.mediated.CFL := indirect.CFL / total.CFL

#Index of moderated mediation
#An alternative way of testing if conditional indirect effects are significantly different from each other
index.mod.med := a3*b1
'

# Fit model
set.seed(1234)
Mod.Med.SEM.promctr.regret <- sem(model = Mod.Med.Lavaan.promctr.regret,
                                     data = cfl,
                                     se = "bootstrap",
                                     bootstrap = 5000)

save(Mod.Med.SEM.promctr.regret, file = "models/regretPromctrFit.RData")
```

```{r med.regret.promctr.lavaan.vis, echo = FALSE, include = FALSE, warning = FALSE, message = FALSE, cache = FALSE}
load("models/regretPromctrFit.RData")
summary(Mod.Med.SEM.promctr.regret,
        fit.measures = FALSE,
        standardize = TRUE,
        estimates = TRUE,
        ci = TRUE,
        rsquare = TRUE)

regretPromctrCoefs <- parameterEstimates(Mod.Med.SEM.promctr.regret)
a3.regret.promctr <- regretPromctrCoefs$est[regretPromctrCoefs$label == "a3"]
a3.p.regret.promctr <- regretPromctrCoefs$pvalue[regretPromctrCoefs$label == "a3"]
b.regret.promctr <- regretPromctrCoefs$est[regretPromctrCoefs$label == "b1"]
b.p.regret.promctr <- regretPromctrCoefs$pvalue[regretPromctrCoefs$label == "b1"]
condIndEffctrl.regret.promctr <- regretPromctrCoefs$est[regretPromctrCoefs$label == "indirect.ctrl"]
condIndEffctrl.se.regret.promctr <- regretPromctrCoefs$se[regretPromctrCoefs$label == "indirect.ctrl"]
condIndEffctrl.cilower.regret.promctr <- regretPromctrCoefs$ci.lower[regretPromctrCoefs$label == "indirect.ctrl"]
condIndEffctrl.ciupper.regret.promctr <- regretPromctrCoefs$ci.upper[regretPromctrCoefs$label == "indirect.ctrl"]
condIndEffCFL.regret.promctr <- regretPromctrCoefs$est[regretPromctrCoefs$label == "indirect.CFL"]
condIndEffCFL.se.regret.promctr <- regretPromctrCoefs$se[regretPromctrCoefs$label == "indirect.CFL"]
condIndEffCFL.cilower.regret.promctr <- regretPromctrCoefs$ci.lower[regretPromctrCoefs$label == "indirect.CFL"]
condIndEffCFL.ciupper.regret.promctr <- regretPromctrCoefs$ci.upper[regretPromctrCoefs$label == "indirect.CFL"]
```

```{r medmodel.regret, include = FALSE}
table2.regret <- regretPromctrCoefs 
table2.regret <- dplyr::rename(table2.regret, Predictor = rhs, Estimate = est, SE = se, p = pvalue, CI.lower = ci.lower, CI.upper = ci.upper)
table2.regret$label <- NULL
table2.regret <- table2.regret[table2.regret$op != "~~",]
table2.regret$Predictor[table2.regret$lhs == "regret.s" & table2.regret$op == "~1"] <- "Intercept"
table2.regret$op[table2.regret$lhs == "regret.s" & table2.regret$op == "~1"] <- "~"
table2.regret$Predictor[table2.regret$lhs == "allo.s" & table2.regret$op == "~1"] <- "Intercept"
table2.regret$op[table2.regret$lhs == "allo.s" & table2.regret$op == "~1"] <- "~"
table2.regret <- table2.regret[table2.regret$op != "~1",]
table2.regret <- table2.regret[1:15,]
table2.regret <- table2.regret %>%
  mutate(section = recode(lhs, regret.s = 1, allo.s = 2,
                          indirect.ctrl = 3, indirect.CFL = 4)) %>%
  arrange(section,desc(op))
table2.regret$Predictor[table2.regret$lhs == "indirect.ctrl"] <- "Control Condition"
table2.regret$Predictor[table2.regret$lhs == "indirect.CFL"] <- "Counterfactual Loss Condition"
table2.regret$Estimate <- myround(table2.regret$Estimate, digits = 2)
table2.regret$SE <- myround(table2.regret$SE, digits = 2)
table2.regret$z <- myround(table2.regret$z, digits = 2)
table2.regret$p <- myround(table2.regret$p, digits = 3)
table2.regret$CI.lower <- myround(table2.regret$CI.lower, digits = 4)
table2.regret$CI.upper <- myround(table2.regret$CI.upper, digits = 4)
table2.regret$p[table2.regret$p < .001] <- "< .001"
table2.regret$Predictor[table2.regret$Predictor == "premc.s"] <- "Prevention Pride"
table2.regret$Predictor[table2.regret$Predictor == "condE"] <- "Counterfactual Loss"
table2.regret$Predictor[table2.regret$Predictor == "promc.s"] <- "Promotion Pride"
table2.regret$Predictor[table2.regret$Predictor == "premc.s:condE"] <- "Prev. Pride x CF Loss"
table2.regret$Predictor[table2.regret$Predictor == "condE:promc.s"] <- "Prom. Pride x CF Loss"
table2.regret$Predictor[table2.regret$Predictor == "regret.s"] <- "Regret"
table2.regret[is.na(table2.regret)] <- ""
table2.regret$lhs <- NULL
table2.regret$op <- NULL
table2.regret$section <- NULL
table2.regret$order <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 13, 10, 11, 12, 14, 15)
table2.regret <- arrange(table2.regret, order)
table2.regret$order <- NULL

medmodel.regret <- table2.regret %>%
  mutate(
    Estimate = cell_spec(Estimate, "latex", align = "r"),
    SE = cell_spec(SE, "latex", align = "r"),
    z = cell_spec(z, "latex", align = "r"),
    p = cell_spec(p, "latex", align = "r"),
    CI.lower = cell_spec(CI.lower, "latex", align = "r"),
    CI.upper = cell_spec(CI.upper, "latex", align = "r")
  ) %>%
  kable("latex", booktabs = TRUE, escape = FALSE, caption = "Summary of Exploratory Mediation Analysis") %>%
  kable_styling(latex_options = c("scale_down")) %>%
  group_rows("Model 1 (DV = Regret)", 1, 6) %>%
  group_rows("Model 2 (DV = Bitcoin Allocation)", 7, 13) %>%
  group_rows("Bootstrapped Conditional Indirect Effects\n(Prev. Pride x CF Loss  Regret  Bitcoin Allocation)", 14, 15) %>%
  row_spec(0, align = "c") %>%
  footnote(general = "This analysis included an effect-coded variable for the counterfactual loss experience: -1 = control, 1 = counterfactual loss. Additionally, all other variables were standardized (M = 0, SD = 1) within this model. Estimated effect sizes for the models reported here are standardized regression coefficients.", general_title = "Note: ", footnote_as_chunk = T, title_format = c("italic"), threeparttable = TRUE, escape = FALSE)
```

```{r, echo = FALSE}
medmodel.regret
```

The interaction between prevention and counterfactual loss was not significantly associated with the degree to which participants reported they regretted not investing in Bitcoin earlier (n.s.), so we concluded that our interaction of interest is not mediated by regret. (See Table 10 for full model output.)

## Exploratory Moderated Mediation Analysis: Hypothetical Happiness

```{r med.happier.promctr.lavaan, eval = FALSE, include = FALSE, warning = FALSE, message = FALSE, cache = TRUE}
# Specify model
Mod.Med.Lavaan.promctr.happier <- '
# Regressions
happier.s ~ 1 + a1*premc.s + a2*condE + a3*premc.s:condE + a4*promc.s + a5*condE:promc.s
allo.s ~ 1 + cdash1*premc.s + cdash2*condE + b1*happier.s + cdash3*premc.s:condE + cdash4*promc.s + cdash5*condE:promc.s

#Indirect effects conditional on moderator (a1 + a3*ModValue)*b1
indirect.ctrl := (a1 + a3*(-1))*b1
indirect.CFL := (a1 + a3*(1))*b1

#Direct effects conditional on moderator (cdash1 + cdash3*ModValue)
direct.ctrl := cdash1 + cdash3*(-1)
direct.CFL := cdash1 + cdash3*(1)

#Total effects conditional on moderator
total.ctrl := direct.ctrl + indirect.ctrl
total.CFL := direct.CFL + indirect.CFL

#Proportion mediated conditional on moderator
#To match the output of "mediate" package
prop.mediated.ctrl := indirect.ctrl / total.ctrl
prop.mediated.CFL := indirect.CFL / total.CFL

#Index of moderated mediation
#An alternative way of testing if conditional indirect effects are significantly different from each other
index.mod.med := a3*b1
'

# Fit model
set.seed(1234)
Mod.Med.SEM.promctr.happier <- sem(model = Mod.Med.Lavaan.promctr.happier,
                                     data = cfl,
                                     se = "bootstrap",
                                     bootstrap = 5000)

save(Mod.Med.SEM.promctr.happier, file = "models/happierPromctrFit.RData")
```

```{r med.happier.promctr.lavaan.vis, echo = FALSE, include = FALSE, warning = FALSE, message = FALSE, cache = FALSE}
load("models/happierPromctrFit.RData")
summary(Mod.Med.SEM.promctr.happier,
        fit.measures = FALSE,
        standardize = TRUE,
        estimates = TRUE,
        ci = TRUE,
        rsquare = TRUE)

happierPromctrCoefs <- parameterEstimates(Mod.Med.SEM.promctr.happier)
a3.happier.promctr <- happierPromctrCoefs$est[happierPromctrCoefs$label == "a3"]
a3.p.happier.promctr <- happierPromctrCoefs$pvalue[happierPromctrCoefs$label == "a3"]
b.happier.promctr <- happierPromctrCoefs$est[happierPromctrCoefs$label == "b1"]
b.p.happier.promctr <- happierPromctrCoefs$pvalue[happierPromctrCoefs$label == "b1"]
condIndEffctrl.happier.promctr <- happierPromctrCoefs$est[happierPromctrCoefs$label == "indirect.ctrl"]
condIndEffctrl.se.happier.promctr <- happierPromctrCoefs$se[happierPromctrCoefs$label == "indirect.ctrl"]
condIndEffctrl.cilower.happier.promctr <- happierPromctrCoefs$ci.lower[happierPromctrCoefs$label == "indirect.ctrl"]
condIndEffctrl.ciupper.happier.promctr <- happierPromctrCoefs$ci.upper[happierPromctrCoefs$label == "indirect.ctrl"]
condIndEffCFL.happier.promctr <- happierPromctrCoefs$est[happierPromctrCoefs$label == "indirect.CFL"]
condIndEffCFL.se.happier.promctr <- happierPromctrCoefs$se[happierPromctrCoefs$label == "indirect.CFL"]
condIndEffCFL.cilower.happier.promctr <- happierPromctrCoefs$ci.lower[happierPromctrCoefs$label == "indirect.CFL"]
condIndEffCFL.ciupper.happier.promctr <- happierPromctrCoefs$ci.upper[happierPromctrCoefs$label == "indirect.CFL"]
```

```{r medmodel.happier, include = FALSE}
table2.happier <- happierPromctrCoefs 
table2.happier <- dplyr::rename(table2.happier, Predictor = rhs, Estimate = est, SE = se, p = pvalue, CI.lower = ci.lower, CI.upper = ci.upper)
table2.happier$label <- NULL
table2.happier <- table2.happier[table2.happier$op != "~~",]
table2.happier$Predictor[table2.happier$lhs == "happier.s" & table2.happier$op == "~1"] <- "Intercept"
table2.happier$op[table2.happier$lhs == "happier.s" & table2.happier$op == "~1"] <- "~"
table2.happier$Predictor[table2.happier$lhs == "allo.s" & table2.happier$op == "~1"] <- "Intercept"
table2.happier$op[table2.happier$lhs == "allo.s" & table2.happier$op == "~1"] <- "~"
table2.happier <- table2.happier[table2.happier$op != "~1",]
table2.happier <- table2.happier[1:15,]
table2.happier <- table2.happier %>%
  mutate(section = recode(lhs, happier.s = 1, allo.s = 2,
                          indirect.ctrl = 3, indirect.CFL = 4)) %>%
  arrange(section,desc(op))
table2.happier$Predictor[table2.happier$lhs == "indirect.ctrl"] <- "Control Condition"
table2.happier$Predictor[table2.happier$lhs == "indirect.CFL"] <- "Counterfactual Loss Condition"
table2.happier$Estimate <- myround(table2.happier$Estimate, digits = 2)
table2.happier$SE <- myround(table2.happier$SE, digits = 2)
table2.happier$z <- myround(table2.happier$z, digits = 2)
table2.happier$p <- myround(table2.happier$p, digits = 3)
table2.happier$CI.lower <- myround(table2.happier$CI.lower, digits = 4)
table2.happier$CI.upper <- myround(table2.happier$CI.upper, digits = 4)
table2.happier$p[table2.happier$p < .001] <- "< .001"
table2.happier$Predictor[table2.happier$Predictor == "premc.s"] <- "Prevention Pride"
table2.happier$Predictor[table2.happier$Predictor == "condE"] <- "Counterfactual Loss"
table2.happier$Predictor[table2.happier$Predictor == "promc.s"] <- "Promotion Pride"
table2.happier$Predictor[table2.happier$Predictor == "premc.s:condE"] <- "Prev. Pride x CF Loss"
table2.happier$Predictor[table2.happier$Predictor == "condE:promc.s"] <- "Prom. Pride x CF Loss"
table2.happier$Predictor[table2.happier$Predictor == "happier.s"] <- "Hypothetical Happiness"
table2.happier[is.na(table2.happier)] <- ""
table2.happier$lhs <- NULL
table2.happier$op <- NULL
table2.happier$section <- NULL
table2.happier$order <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 13, 10, 11, 12, 14, 15)
table2.happier <- arrange(table2.happier, order)
table2.happier$order <- NULL

medmodel.happier <- table2.happier %>%
  mutate(
    Estimate = cell_spec(Estimate, "latex", align = "r"),
    SE = cell_spec(SE, "latex", align = "r"),
    z = cell_spec(z, "latex", align = "r"),
    p = cell_spec(p, "latex", align = "r"),
    CI.lower = cell_spec(CI.lower, "latex", align = "r"),
    CI.upper = cell_spec(CI.upper, "latex", align = "r")
  ) %>%
  kable("latex", booktabs = TRUE, escape = FALSE, caption = "Summary of Exploratory Mediation Analysis") %>%
  kable_styling(latex_options = c("scale_down")) %>%
  group_rows("Model 1 (DV = Hypothetical Happiness)", 1, 6) %>%
  group_rows("Model 2 (DV = Bitcoin Allocation)", 7, 13) %>%
  group_rows("Bootstrapped Conditional Indirect Effects\n(Prev. Pride x CF Loss  Hypothetical Happiness  Bitcoin Allocation)", 14, 15) %>%
  row_spec(0, align = "c") %>%
  footnote(general = "This analysis included an effect-coded variable for the counterfactual loss experience: -1 = control, 1 = counterfactual loss. Additionally, all other variables were standardized (M = 0, SD = 1) within this model. Estimated effect sizes for the models reported here are standardized regression coefficients.", general_title = "Note: ", footnote_as_chunk = T, title_format = c("italic"), threeparttable = TRUE, escape = FALSE)
```

```{r, echo = FALSE}
medmodel.happier
```

The interaction between prevention and counterfactual loss was not significantly associated with the degree to which participants reported they imagine they would be happier if they had invested in Bitcoin earlier (n.s.), so we concluded that our interaction of interest is not mediated by hypothetical happiness. (See Table 11 for full model output.)

## Exploratory Moderated Mediation Analysis: Hypothetical Relief

```{r med.relieved.promctr.lavaan, eval = FALSE, include = FALSE, warning = FALSE, message = FALSE, cache = TRUE}
# Specify model
Mod.Med.Lavaan.promctr.Relieved <- '
# Regressions
relieved.s ~ 1 + a1*premc.s + a2*condE + a3*premc.s:condE + a4*promc.s + a5*condE:promc.s
allo.s ~ 1 + cdash1*premc.s + cdash2*condE + b1*relieved.s + cdash3*premc.s:condE + cdash4*promc.s + cdash5*condE:promc.s

#Indirect effects conditional on moderator (a1 + a3*ModValue)*b1
indirect.ctrl := (a1 + a3*(-1))*b1
indirect.CFL := (a1 + a3*(1))*b1

#Direct effects conditional on moderator (cdash1 + cdash3*ModValue)
direct.ctrl := cdash1 + cdash3*(-1)
direct.CFL := cdash1 + cdash3*(1)

#Total effects conditional on moderator
total.ctrl := direct.ctrl + indirect.ctrl
total.CFL := direct.CFL + indirect.CFL

#Proportion mediated conditional on moderator
#To match the output of "mediate" package
prop.mediated.ctrl := indirect.ctrl / total.ctrl
prop.mediated.CFL := indirect.CFL / total.CFL

#Index of moderated mediation
#An alternative way of testing if conditional indirect effects are significantly different from each other
index.mod.med := a3*b1
'

# Fit model
set.seed(1234)
Mod.Med.SEM.promctr.relieved <- sem(model = Mod.Med.Lavaan.promctr.Relieved,
                                    data = cfl,
                                    se = "bootstrap",
                                    bootstrap = 5000)

save(Mod.Med.SEM.promctr.relieved, file = "models/relievedPromctrFit.RData")
```

```{r med.relieved.promctr.lavaan.vis, echo = FALSE, include = FALSE, warning = FALSE, message = FALSE, cache = TRUE}
load("models/relievedPromctrFit.RData")
summary(Mod.Med.SEM.promctr.relieved,
        fit.measures = FALSE,
        standardize = TRUE,
        estimates = TRUE,
        ci = TRUE,
        rsquare = TRUE)

relievedPromctrCoefs <- parameterEstimates(Mod.Med.SEM.promctr.relieved)
a3.relieved.promctr <- relievedPromctrCoefs$est[relievedPromctrCoefs$label == "a3"]
a3.p.relieved.promctr <- relievedPromctrCoefs$pvalue[relievedPromctrCoefs$label == "a3"]
b.relieved.promctr <- relievedPromctrCoefs$est[relievedPromctrCoefs$label == "b1"]
b.p.relieved.promctr <- relievedPromctrCoefs$pvalue[relievedPromctrCoefs$label == "b1"]
condIndEffctrl.relieved.promctr <- relievedPromctrCoefs$est[relievedPromctrCoefs$label == "indirect.ctrl"]
condIndEffctrl.se.relieved.promctr <- relievedPromctrCoefs$se[relievedPromctrCoefs$label == "indirect.ctrl"]
condIndEffctrl.cilower.relieved.promctr <- relievedPromctrCoefs$ci.lower[relievedPromctrCoefs$label == "indirect.ctrl"]
condIndEffctrl.ciupper.relieved.promctr <- relievedPromctrCoefs$ci.upper[relievedPromctrCoefs$label == "indirect.ctrl"]
condIndEffCFL.relieved.promctr <- relievedPromctrCoefs$est[relievedPromctrCoefs$label == "indirect.CFL"]
condIndEffCFL.se.relieved.promctr <- relievedPromctrCoefs$se[relievedPromctrCoefs$label == "indirect.CFL"]
condIndEffCFL.cilower.relieved.promctr <- relievedPromctrCoefs$ci.lower[relievedPromctrCoefs$label == "indirect.CFL"]
condIndEffCFL.ciupper.relieved.promctr <- relievedPromctrCoefs$ci.upper[relievedPromctrCoefs$label == "indirect.CFL"]
```

```{r medmodel.relieved, include = FALSE}
table2.relieved <- relievedPromctrCoefs 
table2.relieved <- dplyr::rename(table2.relieved, Predictor = rhs, Estimate = est, SE = se, p = pvalue, CI.lower = ci.lower, CI.upper = ci.upper)
table2.relieved$label <- NULL
table2.relieved <- table2.relieved[table2.relieved$op != "~~",]
table2.relieved$Predictor[table2.relieved$lhs == "relieved.s" & table2.relieved$op == "~1"] <- "Intercept"
table2.relieved$op[table2.relieved$lhs == "relieved.s" & table2.relieved$op == "~1"] <- "~"
table2.relieved$Predictor[table2.relieved$lhs == "allo.s" & table2.relieved$op == "~1"] <- "Intercept"
table2.relieved$op[table2.relieved$lhs == "allo.s" & table2.relieved$op == "~1"] <- "~"
table2.relieved <- table2.relieved[table2.relieved$op != "~1",]
table2.relieved <- table2.relieved[1:15,]
table2.relieved <- table2.relieved %>%
  mutate(section = recode(lhs, relieved.s = 1, allo.s = 2,
                          indirect.ctrl = 3, indirect.CFL = 4)) %>%
  arrange(section,desc(op))
table2.relieved$Predictor[table2.relieved$lhs == "indirect.ctrl"] <- "Control Condition"
table2.relieved$Predictor[table2.relieved$lhs == "indirect.CFL"] <- "Counterfactual Loss Condition"
table2.relieved$Estimate <- myround(table2.relieved$Estimate, digits = 2)
table2.relieved$SE <- myround(table2.relieved$SE, digits = 2)
table2.relieved$z <- myround(table2.relieved$z, digits = 2)
table2.relieved$p <- myround(table2.relieved$p, digits = 3)
table2.relieved$CI.lower <- myround(table2.relieved$CI.lower, digits = 4)
table2.relieved$CI.upper <- myround(table2.relieved$CI.upper, digits = 4)
table2.relieved$p[table2.relieved$p < .001] <- "< .001"
table2.relieved$Predictor[table2.relieved$Predictor == "premc.s"] <- "Prevention Pride"
table2.relieved$Predictor[table2.relieved$Predictor == "condE"] <- "Counterfactual Loss"
table2.relieved$Predictor[table2.relieved$Predictor == "promc.s"] <- "Promotion Pride"
table2.relieved$Predictor[table2.relieved$Predictor == "premc.s:condE"] <- "Prev. Pride x CF Loss"
table2.relieved$Predictor[table2.relieved$Predictor == "condE:promc.s"] <- "Prom. Pride x CF Loss"
table2.relieved$Predictor[table2.relieved$Predictor == "relieved.s"] <- "Hypothetical Relief"
table2.relieved[is.na(table2.relieved)] <- ""
table2.relieved$lhs <- NULL
table2.relieved$op <- NULL
table2.relieved$section <- NULL
table2.relieved$order <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 13, 10, 11, 12, 14, 15)
table2.relieved <- arrange(table2.relieved, order)
table2.relieved$order <- NULL

medmodel.relieved <- table2.relieved %>%
  mutate(
    Estimate = cell_spec(Estimate, "latex", align = "r"),
    SE = cell_spec(SE, "latex", align = "r"),
    z = cell_spec(z, "latex", align = "r"),
    p = cell_spec(p, "latex", align = "r"),
    CI.lower = cell_spec(CI.lower, "latex", align = "r"),
    CI.upper = cell_spec(CI.upper, "latex", align = "r")
  ) %>%
  kable("latex", booktabs = TRUE, escape = FALSE, caption = "Summary of Exploratory Mediation Analysis") %>%
  kable_styling(latex_options = c("scale_down")) %>%
  group_rows("Model 1 (DV = Hypothetical Relief)", 1, 6) %>%
  group_rows("Model 2 (DV = Bitcoin Allocation)", 7, 13) %>%
  group_rows("Bootstrapped Conditional Indirect Effects\n(Prev. Pride x CF Loss  Hypothetical Relief  Bitcoin Allocation)", 14, 15) %>%
  row_spec(0, align = "c") %>%
  footnote(general = "This analysis included an effect-coded variable for the counterfactual loss experience: -1 = control, 1 = counterfactual loss. Additionally, all other variables were standardized (M = 0, SD = 1) within this model. Estimated effect sizes for the models reported here are standardized regression coefficients.", general_title = "Note: ", footnote_as_chunk = T, title_format = c("italic"), threeparttable = TRUE, escape = FALSE)
```

```{r, echo = FALSE}
medmodel.relieved
```

When we control for promotion pride and the interaction between promotion and counterfactual loss, the interaction between prevention and counterfactual loss was significantly associated with the degree to which participants reported they imagine they would be relieved if they had invested in Bitcoin earlier ($\beta = `r myround(a3.relieved.promctr, digits = 2)`$, $`r pval(as.numeric(a3.p.relieved.promctr))`$), and the effect of participants reporting they imagined being relieved if they had invested earlier ($\beta = `r myround(b.relieved.promctr, digits = 2)`$, $`r pval(as.numeric(b.p.relieved.promctr))`$) on Bitcoin allocation was also significant. (See Table 12 and the article for full model output.)

# Rerunning with Participants Who Learned About Study from Other M-Turk workers.

## Primary Linear Analysis

The direction and significance of our primary linear analysis does not change when rerunning the analysis to include participants who learned about the study from other M-Turk workers (see Table 13 and Figure 2).

```{r subset4.rerun, include=FALSE}
# Creating subset to facilitate visualization of results within each condition
cfl.rerun.cflcond <- subset(cfl.rerun, condition == "CF Loss") # n = 144
cfl.rerun.ctrlcond <- subset(cfl.rerun, condition == "Control") # n = 157
```

```{r save.rerun, echo=FALSE}
# SAVING CLEAN DATASETS
save(cfl.rerun, cfl.rerun.cflcond, cfl.rerun.ctrlcond, file = "data/rfcfloss_rerun_clean.RData")
write.csv(cfl.rerun, file = "data/rfcfloss_rerun_clean.csv")
```

```{r primarymodel.rerun, include = FALSE}
# PRIMARY MODEL, CONTROLLING FOR PROMOTION (mean-centered RF and dummy-coded condition)
rfcfl.promctr.rerun <- lm(allo ~ premc * condD + promc * condD, data=cfl.rerun)
summary(rfcfl.promctr.rerun) # premc:condD b = -11.973, p = .0292
```

```{r primarymodelreruntable, include = FALSE}
table1r <- tidy(rfcfl.promctr.rerun)
table1r <- dplyr::rename(table1r, Predictor = term, Estimate = estimate, SE = std.error, t = statistic, p = p.value)
table1r$Estimate <- myround(table1r$Estimate, digits = 2)
table1r$SE <- myround(table1r$SE, digits = 2)
table1r$t <- myround(table1r$t, digits = 2)
table1r$p <- myround(table1r$p, digits = 3)
table1r$p[table1r$p < .001] <- "< .001"
table1r$Predictor[table1r$Predictor == "(Intercept)"] <- "Intercept"
table1r$Predictor[table1r$Predictor == "premc"] <- "Prevention Pride"
table1r$Predictor[table1r$Predictor == "condD"] <- "Counterfactual Loss"
table1r$Predictor[table1r$Predictor == "promc"] <- "Promotion Pride"
table1r$Predictor[table1r$Predictor == "premc:condD"] <- "Prevention Pride x Counterfactual Loss"
table1r$Predictor[table1r$Predictor == "condD:promc"] <- "Promotion Pride x Counterfactual Loss"
table1r[is.na(table1r)] <- ""
table1r$order <- c(1, 2, 3, 5, 4, 6)
table1r <- arrange(table1r, order)
table1r$order <- NULL
```

```{r primarymodelrerunprint, echo = FALSE, include = TRUE, results = 'asis'}
apa_table(table1r, caption = "RERUN: Summary of Linear Regression Analysis", note = "This analysis included a dummy-coded variable for the counterfactual loss manipulation: 0 = control, 1 = counterfactual loss. Additionally, prevention and promotion pride were mean-centered within this model. Estimated effect sizes reported here are unstandardized regression coefficients.", align = 'lrrrr')
```

```{r primarymodelplot.rerun, echo = FALSE}
pred.data.ctrl.rerun <- data.frame(premc = seq(min(cfl.rerun$premc, na.rm=T), 
                                         max(cfl.rerun$premc, na.rm=T), .1),
                                         promc = 0, condD = 0, condition = "Control")
rfcfl.promctr.pred.ctrl.rerun <- cbind(pred.data.ctrl.rerun, 
                                 predict(rfcfl.promctr.rerun, pred.data.ctrl.rerun, 
                                         interval = "confidence", 
                                         type = c("response", "terms")))
rfcfl.promctr.pred.ctrl.rerun <- dplyr::rename(rfcfl.promctr.pred.ctrl.rerun, allo = fit)

pred.data.CFL.rerun <- data.frame(premc = seq(min(cfl.rerun$premc, na.rm=T), 
                                        max(cfl.rerun$premc, na.rm=T), .1),
                                        promc = 0, condD = 1, condition = "CF Loss")
rfcfl.promctr.pred.CFL.rerun <- cbind(pred.data.CFL.rerun, 
                                predict(rfcfl.promctr.rerun, pred.data.CFL.rerun, 
                                        interval = "confidence", 
                                        type = c("response", "terms")))
rfcfl.promctr.pred.CFL.rerun <- dplyr::rename(rfcfl.promctr.pred.CFL.rerun, allo = fit)

primarymodel.rerun <- ggplot(data=cfl.rerun, aes(x=premc, y=allo)) +
       scale_color_manual(values=c("gray0", "gray50")) +
       geom_ribbon(data = rfcfl.promctr.pred.ctrl, aes(ymin = lwr, ymax = upr), alpha = .3, fill = "gray") +
       geom_ribbon(data = rfcfl.promctr.pred.CFL, aes(ymin = lwr, ymax = upr), alpha = .3, fill = "gray") +
       geom_line(data = rfcfl.promctr.pred.ctrl, aes(color=condition), size = 1) +
       geom_line(data = rfcfl.promctr.pred.CFL, aes(color=condition), size = 1) +
       labs(title="RERUN: Prevention Pride and Counterfactual Loss as\nPredictors of Bitcoin Allocation\n(Controlling for Promotion Pride and the Interaction\nBetween Promotion Pride and Counterfactual Loss)", x="Prevention Pride (Mean-Centered)", y="Bitcoin Allocation (%)", color = "Condition")
```

```{r primarymodelplot_print.rerun, echo = FALSE, include = TRUE, fig.cap = "RERUN: Predicted Bitcoin allocation by prevention pride and counterfactual loss experience, controlling for promotion pride and the interaction between promotion pride and counterfactual loss.", fig.align = "center", out.width = '90%', out.height = '90%'}
primarymodel.rerun
```

## Simple Slopes and Johnson-Neyman Analyses

```{r jn1_simpleslopes.rerun, echo = FALSE}
jn1.rerun <- sim_slopes(model = rfcfl.promctr.rerun, pred = premc, modx = condD, modx.values = c(0,1),
           centered = "all", data = cfl, cond.int = FALSE,
           johnson_neyman = FALSE, jnplot = FALSE, jnalpha = 0.05, robust = FALSE,
           digits = getOption("jtools-digits", default = 2), pvals = TRUE,
           confint = TRUE, ci.width = 0.95)
jn1.rerun <- tidy(jn1.rerun)
```

```{r jn2, echo = FALSE}
rfcfl.promctr.nonstd.rerun <- lm(allo ~ prev * condD + promc * condD, data=cfl.rerun)
jn2.rerun <- sim_slopes(model = rfcfl.promctr.nonstd.rerun, pred = condD, modx = prev, modx.values = c(2.50991, 3.43, 4.572230), 
           centered = "all", data = cfl, cond.int = FALSE,
           johnson_neyman = TRUE, jnplot = TRUE, jnalpha = 0.05, robust = FALSE,
           digits = getOption("jtools-digits", default = 2), pvals = TRUE,
           confint = TRUE, ci.width = 0.95)
jncutoff_low.rerun <- jn2.rerun$jn[[1]]$bounds[1]
jncutoff_high.rerun <- jn2.rerun$jn[[1]]$bounds[2]
jn2.rerun <- tidy(jn2.rerun)
```

When rerunning our simple slopes and Johnson-Neyman analyses, the direction and significance of our results do not change. The effect of prevention pride on Bitcoin allocation was still significant in the counterfactual loss condition ($B = `r myround(jn1.rerun[1,"estimate"], digits = 2)`, SE = `r myround(jn1.rerun[1,"std.error"], digits = 2)`, t = `r myround(jn1.rerun[1,"statistic"], digits = 2)`, `r pval(as.numeric(jn1.rerun[1,"p.value"]))`$; 95% CI [`r myround(jn1.rerun[1,"conf.low"], digits = 4)`, `r myround(jn1.rerun[1,"conf.high"], digits = 4)`]) but non-significant in the control condition.

Further, the conditional effect of counterfactual loss on Bitcoin allocation was still positive for people with prevention pride of less than 2.51 ($B = `r myround(jn2.rerun[3,"estimate"], digits = 2)`, SE = `r myround(jn2.rerun[3,"std.error"], digits = 2)`, t = `r myround(jn2.rerun[3,"statistic"], digits = 2)`, `r pval(as.numeric(jn2.rerun[3,"p.value"]))`$), and negative for people with prevention pride of greater than 4.57 ($B = `r myround(jn2.rerun[1,"estimate"], digits = 2)`, SE = `r myround(jn2.rerun[1,"std.error"], digits = 2)`, t = `r myround(jn2.rerun[1,"statistic"], digits = 2)`, `r pval(as.numeric(jn2.rerun[1,"p.value"]))`$).

## Exploratory Mediation Analysis (Hayes PROCESS Model 8): Counterfactual Relief

```{r med.relieved.promctr.lavaan.rerun, eval = FALSE, include = FALSE, warning = FALSE, message = FALSE, cache = TRUE}
# Fit model (no changes in model from original specification)
set.seed(1234)
Mod.Med.SEM.promctr.relieved.rerun <- sem(model = Mod.Med.Lavaan.promctr.Relieved,
                                    data = cfl.rerun,
                                    se = "bootstrap",
                                    bootstrap = 5000)

save(Mod.Med.SEM.promctr.relieved.rerun, file = "models/relievedPromctrFitRerun.RData")
```

```{r med.relieved.promctr.lavaan.vis.rerun, echo = FALSE, include = FALSE, warning = FALSE, message = FALSE, cache = FALSE}
load("models/relievedPromctrFitRerun.RData")
summary(Mod.Med.SEM.promctr.relieved.rerun,
        fit.measures = FALSE,
        standardize = TRUE,
        estimates = TRUE,
        ci = TRUE,
        rsquare = TRUE)

relievedPromctrCoefs.rerun <- parameterEstimates(Mod.Med.SEM.promctr.relieved.rerun)
a3.relieved.promctr.rerun <- relievedPromctrCoefs.rerun$est[relievedPromctrCoefs.rerun$label == "a3"]
a3.p.relieved.promctr.rerun <- relievedPromctrCoefs.rerun$pvalue[relievedPromctrCoefs.rerun$label == "a3"]
b.relieved.promctr.rerun <- relievedPromctrCoefs.rerun$est[relievedPromctrCoefs.rerun$label == "b1"]
b.p.relieved.promctr.rerun <- relievedPromctrCoefs.rerun$pvalue[relievedPromctrCoefs.rerun$label == "b1"]
condIndEffctrl.relieved.promctr.rerun <- relievedPromctrCoefs.rerun$est[relievedPromctrCoefs.rerun$label == "indirect.ctrl"]
condIndEffctrl.se.relieved.promctr.rerun <- relievedPromctrCoefs.rerun$se[relievedPromctrCoefs.rerun$label == "indirect.ctrl"]
condIndEffctrl.cilower.relieved.promctr.rerun <- relievedPromctrCoefs.rerun$ci.lower[relievedPromctrCoefs.rerun$label == "indirect.ctrl"]
condIndEffctrl.ciupper.relieved.promctr.rerun <- relievedPromctrCoefs.rerun$ci.upper[relievedPromctrCoefs.rerun$label == "indirect.ctrl"]
condIndEffCFL.relieved.promctr.rerun <- relievedPromctrCoefs.rerun$est[relievedPromctrCoefs.rerun$label == "indirect.CFL"]
condIndEffCFL.se.relieved.promctr.rerun <- relievedPromctrCoefs.rerun$se[relievedPromctrCoefs.rerun$label == "indirect.CFL"]
condIndEffCFL.cilower.relieved.promctr.rerun <- relievedPromctrCoefs.rerun$ci.lower[relievedPromctrCoefs.rerun$label == "indirect.CFL"]
condIndEffCFL.ciupper.relieved.promctr.rerun <- relievedPromctrCoefs.rerun$ci.upper[relievedPromctrCoefs.rerun$label == "indirect.CFL"]
```

```{r medmodel.relieved.rerun, echo = FALSE, include = FALSE}
table2.relieved.rerun <- relievedPromctrCoefs.rerun
table2.relieved.rerun <- dplyr::rename(table2.relieved.rerun, Predictor = rhs, Estimate = est, SE = se, p = pvalue, CI.lower = ci.lower, CI.upper = ci.upper)
table2.relieved.rerun$label <- NULL
table2.relieved.rerun <- table2.relieved.rerun[table2.relieved.rerun$op != "~~",]
table2.relieved.rerun$Predictor[table2.relieved.rerun$lhs == "relieved.s" & table2.relieved.rerun$op == "~1"] <- "Intercept"
table2.relieved.rerun$op[table2.relieved.rerun$lhs == "relieved.s" & table2.relieved.rerun$op == "~1"] <- "~"
table2.relieved.rerun$Predictor[table2.relieved.rerun$lhs == "allo.s" & table2.relieved.rerun$op == "~1"] <- "Intercept"
table2.relieved.rerun$op[table2.relieved.rerun$lhs == "allo.s" & table2.relieved.rerun$op == "~1"] <- "~"
table2.relieved.rerun <- table2.relieved.rerun[table2.relieved.rerun$op != "~1",]
table2.relieved.rerun <- table2.relieved.rerun[1:15,]
table2.relieved.rerun <- table2.relieved.rerun %>%
  mutate(section = recode(lhs, relieved.s = 1, allo.s = 2,
                          indirect.ctrl = 3, indirect.CFL = 4)) %>%
  arrange(section,desc(op))
table2.relieved.rerun$Predictor[table2.relieved.rerun$lhs == "indirect.ctrl"] <- "Control Condition"
table2.relieved.rerun$Predictor[table2.relieved.rerun$lhs == "indirect.CFL"] <- "Counterfactual Loss Condition"
table2.relieved.rerun$Estimate <- myround(table2.relieved.rerun$Estimate, digits = 2)
table2.relieved.rerun$SE <- myround(table2.relieved.rerun$SE, digits = 2)
table2.relieved.rerun$z <- myround(table2.relieved.rerun$z, digits = 2)
table2.relieved.rerun$p <- myround(table2.relieved.rerun$p, digits = 3)
table2.relieved.rerun$CI.lower <- myround(table2.relieved.rerun$CI.lower, digits = 4)
table2.relieved.rerun$CI.upper <- myround(table2.relieved.rerun$CI.upper, digits = 4)
table2.relieved.rerun$p[table2.relieved.rerun$p < .001] <- "< .001"
table2.relieved.rerun$Predictor[table2.relieved.rerun$Predictor == "premc.s"] <- "Prevention Pride"
table2.relieved.rerun$Predictor[table2.relieved.rerun$Predictor == "condE"] <- "Counterfactual Loss"
table2.relieved.rerun$Predictor[table2.relieved.rerun$Predictor == "promc.s"] <- "Promotion Pride"
table2.relieved.rerun$Predictor[table2.relieved.rerun$Predictor == "premc.s:condE"] <- "Prev. Pride x CF Loss"
table2.relieved.rerun$Predictor[table2.relieved.rerun$Predictor == "condE:promc.s"] <- "Prom. Pride x CF Loss"
table2.relieved.rerun$Predictor[table2.relieved.rerun$Predictor == "relieved.s"] <- "Hypothetical Relief"
table2.relieved.rerun[is.na(table2.relieved.rerun)] <- ""
table2.relieved.rerun$lhs <- NULL
table2.relieved.rerun$op <- NULL
table2.relieved.rerun$section <- NULL
table2.relieved.rerun$order <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 13, 10, 11, 12, 14, 15)
table2.relieved.rerun <- arrange(table2.relieved.rerun, order)
table2.relieved.rerun$order <- NULL

medmodel.relieved.rerun <- table2.relieved.rerun %>%
  mutate(
    Estimate = cell_spec(Estimate, "latex", align = "r"),
    SE = cell_spec(SE, "latex", align = "r"),
    z = cell_spec(z, "latex", align = "r"),
    p = cell_spec(p, "latex", align = "r"),
    CI.lower = cell_spec(CI.lower, "latex", align = "r"),
    CI.upper = cell_spec(CI.upper, "latex", align = "r")
  ) %>%
  kable("latex", booktabs = TRUE, escape = FALSE, caption = "Summary of Exploratory Mediation Analysis") %>%
  kable_styling(latex_options = c("scale_down")) %>%
  group_rows("Model 1 (DV = Hypothetical Relief)", 1, 6) %>%
  group_rows("Model 2 (DV = Bitcoin Allocation)", 7, 13) %>%
  group_rows("Bootstrapped Conditional Indirect Effects\n(Prev. Pride x CF Loss  Hypothetical Relief  Bitcoin Allocation)", 14, 15) %>%
  row_spec(0, align = "c") %>%
  footnote(general = "This analysis included an effect-coded variable for the counterfactual loss experience: -1 = control, 1 = counterfactual loss. Additionally, all other variables were standardized (M = 0, SD = 1) within this model. Estimated effect sizes for the models reported here are standardized regression coefficients.", general_title = "Note: ", footnote_as_chunk = T, title_format = c("italic"), threeparttable = TRUE, escape = FALSE)
```

```{r medmodel.relieved.rerun.print, echo = FALSE}
medmodel.relieved.rerun
```

When we control for promotion pride and the interaction between promotion and counterfactual loss, the interaction between prevention and counterfactual loss was still significantly associated with the degree to which participants reported they would be relieved if they had invested in Bitcoin earlier ($\beta = `r myround(a3.relieved.promctr.rerun, digits = 2)`$, $`r pval(as.numeric(a3.p.relieved.promctr.rerun))`$), and the effect of participants reporting they would be relieved if they had invested earlier ($\beta = `r myround(b.relieved.promctr.rerun, digits = 2)`$, $`r pval(as.numeric(b.p.relieved.promctr.rerun))`$) on Bitcoin allocation was also significant.

The indirect effect of prevention on Bitcoin allocation through reporting relief if they had invested earlier was significant and negative for individuals in the counterfactual loss condition ($\beta = `r myround(condIndEffCFL.relieved.promctr.rerun, digits = 2)`$, $SE = `r myround(condIndEffCFL.se.relieved.promctr.rerun, digits = 2)`$, 95% $CI = `r myround(condIndEffCFL.cilower.relieved.promctr.rerun, digits = 4)`, `r myround(condIndEffCFL.ciupper.relieved.promctr.rerun, digits = 4)`$), but not for individuals in the control condition (n.s.). This indicates that the moderation is still fully mediated.

```{r references, echo = FALSE, results='asis'}
cat("\\newpage")
cat("# References")
```

```{r create_r-references, echo = FALSE, results='asis'}
r_refs(file = "manuscript/rfcfloss.bib")
```

<div id = "refs"></div>